\chapter*{I'm Right Here}

\section*{Meetings}

I don't really remember the first time that I met Sasha. There wasn't anything particularly special about her. She was taller and faster than me and that made me a bit jealous. I told my mom later that there was a new girl in our class and that she was dumb. My mother, in her disapproving, yet gentle, way told me to be nice and just stay away from her if it bothered me that much.

So, like any self-respecting six year old boy, I threw rocks at her. Most of the time they were small rocks, pebbles really, that would harmlessly bounce off. I could see that she noticed and was a bit flummoxed by it. \textit{``Why are you throwing things at me?''} I imagined her saying. The thought made me giggle with silent amusement. Jason said that if I really wanted her to notice, I'd have to throw a bigger rock. So, looking around, I looked for the biggest rock that I thought would be safe to throw. It feld nice and solid; surely this one would get her attention.

With litte more than second thought, my arm slung the rock through the air toward Sasha, who was currently playing hop-scotch with some other girls. The rock I picked must have been the Ferrari of rocks, because it flew so beautifully, not veering an inch from its intended trajectory. I was magnificent, until I heard the solid thud followed by the tink of it hitting the ground. The rock didn't look so beautiful in that moment, but I didn't want to tear my eyes from it. I didn't want to look at Sasha's face. I could feel her gaze: hard, fast, and unbroken. I wanted to run away from my actions, but my legs wouldn't move. Even if I did run, she was faster than me. I'm sure she would run me down and hit me. I didn't want to look up, but I could hear the teachers assembling for aid and retribution. I needed to look up and at least see my handiwork and why I would be punished.

Her toes were pointed together and knees shaking. White-knuckled fists bunched her dandilion print sundress, the collar of which was now wet. The tawny pigtails that her mother put up were still tight, but not nearly as much as her countenance. She looked as though she were about to erupt, but not with anger. She looked disappointed and pained at the thought that someone would do such a thing. How could I have done that. Stupid Jason. How could you talk me into doing something so mean. I couldn't apologize right now, could I? I mean, she wouldn't accept it. I wouldn't accept it if I were in her shoes.

My eyes darted back to my feet as the teachers arrived on the scene. There was no escape. I was in trouble. I was dead. My father was going to kill me.

Looking back up at her face to see once more as I signed out my short life, I could see that the tightness that had been her composure had now melted to soft sobbing into Mrs. Gooseman's dress. With her head turned to the side, I could see a faint red patch underneath her brown hair of where my ``Ferrari'' had made contact.
