\chapter*{The Old Woman}

% an old woman in a small secluded town (unbeknownst to the villagers) transports people once coming of age to an alternate dimension that is a disturbing mockery of the town and life they once had

If you were to take the worn, east-ward road out of Langton to its end and then continued upon the game trail, the week's journey would bring you to Gransford. Seamlessly coddled by cliffs upon one side and forest on the other, the time forlorn community, resilient in traditions and superstitions, refuses to be snuffed from existence. It's very existence secluded or ignored by the world beyond, exemplified by its absence of visitors or the like. Depending on whom you were to ask, this was a prison or a palace. The trees upon the one edge being bars or castle walls; the cliffs either a moat or expanse.

Many of the trees on the skirting edge of the forest were younger and oft provided a place for the children to play as the kids would imagine them to be lost friends of times long past. Sometimes, at the setting sun, the last rays of daylight would flick across the new trees, puppeteering the shadows into dances until their finale at the sun's ultimate descent. The kids found particular joy in playing amongst shadowy kinsfolk, dancing until their parents drew them in for the night.

As the children grew, they would bid farewell to their coniferous playmates, dawn Medallions of Plenty, and find their way to the fishing cliffs. There they would find perch upon the worn ground, dangle their eager legs, and dream the day away, fishing amongst the elderly. Their dreams would grow, just as their bodies, from the frivolities of tag and hide-and-seek to marriage and bringing forth children of their own. Little was as unmovable as the sediment of the shorn coastline, perhaps save the cycle of life in this quiet, forgotten corner of the world.

Life in Gransford is quaint, quiet, and immutable. All was, is, and will continue to be the same and each resident held the same fate. Oft I would contemplate the simplicity of this life as I sit upon my perch, grazing the depths below.
