\chapter*{The Old Woman}

% an old woman in a small secluded town (unbeknownst to the villagers) transports people once coming
% of age to an alternate dimension that is a disturbing mockery of the town and life they once had

A week's journey by foot past the end of the dirt trail outside Langton would bring you to the small
town of Gransford. Far from any man's wishes or desires, here, nestled amongst the fishing
cliffs, a small community resilient in traditions and superstitions refueses to be snuffed from
existence.

I was born in this town, but then again, everyone else shared a similar fate. As far as I can
remember, no one ever visited and no one ever left; at least before the age fourty. Life is
relatively mundane as the Jeswalops and Grishams rarely had tussles anymore. William was always the
trouble maker and loved the tussles. I personally think that he did it to break up the monotony of
day to day life. He never was one for fishing. Something about the ten pound sinker we had to attach
to the lines rubbed him the wrong way. Once I made the mistake of speaking to him on a fishing trip
and he threatened to use me as the sinker instead.

Despite all his murmurings, not even he would ever question lady Yağmur. She didn't have a last name
and seemed to be as neutral in all things as her appearance. She never took sides, but gave advice
and council fairly. It was all to be expected, however, being the eldest person in the town, but by
how much, no one knew. All of the adults would steal themselves away to the neighboring towns upon
their fourtieth birthdays to experience the outside world. Lady Yağmur was special as she was the
only person to love the town enough to return after her venture. I expect William ran the week's
journey to the dirt trail leading to Langton and from there never looked back. He hated this place.
Few people hated this place as much as he, but we were warned that outside was no place for us
fledgling souls.

We were all warned from an early age that the outside world was beautiful and magnificent, but was
not to be taken lightly for all its gaudy brilliance, a wretched underbelly stood waiting to enslave
the timid and weak. For this reason, at the ripe age of fourty, lady Yağmur would give her blessing
and send each person, armed with knowledge and blessing, into the outside world for their maturity
gave them a fortitude of mind to withstand.

Would I return to Gransford after seeing the outside world or would I be ensared by my lust for
riches of mind and body? I hoped that I wouldn't for I was sure that was the way to damnation. I'm
sure that I would return. I would be strong. I would look up on that world and know that I have the
virtue of the holy knights of old. But, what of my mother? Was she not devout to the traditions of
our village? I heard from others that in my infantile years, she would often return from fishing
trips at the cliffs with baskets of fish for all. Lady Yağmur would say that she was fertile beyond 
compare and it was thanks to her devotion to the innocence of Gransford. She even received a greater
medallion to harness her virtues. Despite all this, why did my mother, of all people, not return
from the outer lands?

I soon would celebrate another celestial elipse and would be one more year closer to my fourtieth
year. I too would receive blessing and knowledge and be sent into the embrace of tempation. Despite
brandishing a smaller medallion, I believe that deep down, I have drive that is yet secret to the
eye of Yağmur. Should I happen upon my mother in my ventures, I will bring her back, much like the
knights of old with their chivalric honors, to restore her innocence and peace.

``Jarom!''

Startling awake from my terse ruminations, I found Zachary Edison grasping my rod, keeping it from
falling great distance to the waters below.

``You going to stop day dreaming about Jennifer and help me bring in your libation?''

``Uh, yeah. Sorry.''

After a small quarrel and a few minutes of reeling, a smaller than average fish was added to my dry
basket.

``So, how was it?''

``How was what?''

``You know. Your daydream? About Jennifer?''

``Don't be distasteful. I wasn't thinking anything weird about Jennifer.''

``Why not? You two did get married just a month ago. If not thinking about her, then what?''

``Would you leave me alone if I told you that you were right? That I was thinking weird things about
my... wife?'' The word still felt sticky coming from my tongue. I did wait quite a bit longer to get
married than most of the other men in the village, who typically were wed by their twenty-second
birthday. Being so much older, I also had to marry a girl quite a bit younger than myself, and I
felt that Zachary was just a little jealous.

``No. I would not. Now that you were obviously thinking about something else. I swear, I would do
nothing but think of her if I married a young thing like that. So what was it?''

``Do you oft think about the outside world and whether you'll come back to Gransford?''

``Not really. I have bitter taste this place. And I don't particularly care for old lady Yağmur
either. I'll likely get whatever knowledge she has for me and depart with my family at my heel.''

``Come on, you can't do that to your kids. They're not old enough and will surely sucumb to
something.''

``Bah. I'd take care of them. You know that. I'd never let anything happen to my boys.''

``I certainly hope so. For your sake. Can you image how upset lady Yağmur is going to be when she
realizes that you took your family before they reached the age of maturity?''

``Frankly, I don't care, because there's no chance that I, or my family, will ever return.''

``Well, it's getting dark. We should take our fish back for the Libation.''

``Yeah, I guess. Always hated this ceremony. I don't like the way lady Yağmur blinks during
collection.''

\noindent\rule{\textwidth}{1pt}

The day of Zachary's fourtieth came and went, but contrary to the words imparted to me on the
cliffside, his family remained in Gransford and he left on his journey alone. I thought surely he's
being reasonable, testing the waters of the outside world before coming back and stealing his family
away, if he were still beset to such a frivolous plan.

One thing that he said did set me on edge, akin to wondering if the firewood was covered before
getting into bed before a downpour. There was something \textit{off} about lady Yağmur. He had
mentioned the way that she blinks during the Libation, but the closer I watched her,
the itchier I got.

The way she blinks? I watched as closely as I could over the last year or so, but I couldn't quite
put my finger on what was \textit{wrong}. Was it that when he blinked, her upper eyelids didn't come
down to meet her bottom, or was it that her side eyelids rotated upward to meet her top eyelids?
Something just wasn't right.

And the more that I thought about it, other things seemed odd. How old was lady Yağmur? She told us
that she went through her own visit to the outside world, but no one knew how long ago that had
been. No one seemed to know how old she was. She certainly looked old, but I didn't really know what
old people were supposed to look like. None of us had ever seen anyone return from a outer world
trip, save her. So were old people supposed to have wrinkly skin? Her skin was certainly wrinkled.
Around her eyes were a great many lines, but I guessed they had accumulated from the years of worry
and joy she had experienced. Were old people supposed to have wrinkly teeth? No one I knew had
wrinkly teeth, but we were all young in comparison. I had always supposed they came from years of mastication.

Day after day, I would observe her when I could, and night after night, I would lay awake trying to
understand what was wrong. When I would look at her, the closer I looked, the more I found myself
unable to focus on her. Once, I believed I was looking at a mirage, a cruel refraction to dissuade
me from my ceaseless inspection.

In my torment, I began to worry for my soul as my fourtieth solar round approached. Did lady
Yağmur know of my vacillations? Would she send me on my journey ill prepared as punishment for my
hubris? Certainly she would not. She has always been fair in all her dealings. But the more I dwelt
on Zachary's simple words, the more I slipped into disillusion and ambiguity. For solace, I broke
for the singular white ash tree at the cliffs where my mother used to take me more and more
regularly. There, and only there, I could sense peace.

\noindent\rule{\textwidth}{1pt}

``Jarom. Within thine heart, I perceive disproportionate distress to one of thine circumstances.
Corroborating the inkling within mine toe, Jennifer has confided that marital celebrations have, of
late, been diminuitive. What fouls thine glow?''

``Lady Yağmur,'' not making eye contact, ``I am just worried about my venture to the outer world.''

``Alas, the time wanes nigh, does it not?''

``It does. Tomorrow.'' She was close enough that I could feel her blinking in my periphery, but nary
the scent of her breath.

``To abate the tumult within thine soul, midst the Libation at dusk, cast thine eyes toward the sod
not. Rejoice and behold.''

``Thank you, lady Yağmur.'' What else could I say? Was this issued just for me or did every person
on the eve of their venture receive such a request? Was this the knowledge that was to be imparted
before exodus?

I ran to the ash tree to find respite, but today none came. My mand crashed with each break of the
ocean upon the cliffs. What would I see? Would I discover the cause of anguish within my mind and
dispell it? Is there something wrong with lady Yağmur, or is the fault within my cognizance? Oh
could I unlive Zachary's words. Zachary's dumb, simple words. I cursed him for his negligence, but
he was gone and could pay not for his crime.

\noindent\rule{\textwidth}{1pt}

The hours leading to the Libation waxed long in a delirium of foreboding and nausea, but the hour
did arrive and I did make my way to the small altered amphitheater near the cliffside. Upon arrival,
lady Yağmur made a gesture to sit near the altar that implied many too many joints within her arm. I
did not fully recognize this until I had made near and rested myself in genuflection upon the stony
earth.

When the ceremony began, I did not bow my head in resolution as the others did, but gazed on with
morbid anticipation.

% Gods! To protect innocence, spirit, and light, this libation we bring. Give blessing to those who
% partake.
``\textit{Tanrılar!}'' began lady Yağmur. ``\textit{Masumiyeti, ruhu ve ışığı korumak için
getirdiğimiz bu içkiyi. Katılanları kutsayın.}''

The words, yet foreign, were familiar to me for I had heard them since my youth, but today,
seeing the words drip from her tongues, I prayed for my rapture.

Bringing the first fish to her lips, lady Yağmur, with razor precision ripped the gut open with her
fangs. The blood upon her lips shone with a brilliant red that I had never before seen. Fish by fish,
her fingers intertwined into a tourniquet about the lifeless meat before exacting the incision, all
the while, the masses apart from me bowed their heads in supplication. With each fish my horror
exacerbated to the point that I thought I would expell all the breath within my chest just to tear
my eyes from the scene, but as if in a nightmare, my terrestrial body stationed upon the ground,
eyes untenably affixed to the rites.

Wiping her mouth with the inside of her woolen sleeve, she bade all stand and gather the newly cut
fish. Then, as with each night, the head of each household came and took what fish was needed for
sustenance, and dumped the entrails into the ocean speaking, ``\textit{Seni beslerim.}''

A chill so violent flew up my spine that I wished it and myself gone, but I knew that I would need
to collect for myself and Jennifer, for no other nourishment was to be found within our pantry.

What was I supposed to glean from such an experience? What was going on? Why didn't any one else
know what was going on? Was I obligated to tell someone? Should I tell \textit{Jennifer}? My poor,
defenseless, innocent wife? Would she even believe me? She had already been given a greater
medallion, like unto my mother during her youth. Would she trust me, her husband, over lady Yağmur?
Should I bestow my faithlessness upon my wife, who being destitue of doubt, likely would not
comprehend? No, it is better for her to not be as me, the damned, the 

``Jarom.'' Cut off mid thought by the beckoning of she who ravaged my sanity. ``I entreat thee,
partake, for thine stewardship and thineself. The splinters of insight have now been showered upon
thee and on the morrow, thine journey awaits. And forget not thine medallion.''

Almost without hesitation, my body recoiled against reviling of my mind into habitual motion, taking
the fish and reciting the incantation languidly.

\noindent\rule{\textwidth}{1pt}

That night, lying in bed, I scare believed that I would ever be able to sleep again. Jennifer
worried about me for I had been acting strangely the past few months, and tonight, according to her,
I was nearly catatonic. I should have tried to eat something to ease her mind, but I could not
stomach the thought of eating any product of the Libation.

Thinking, during the Libation, it was the first time that I could clearly see lady Yağmur. Her form
was bent and protruding in places that none of the young folk could resemble. What was she? What was
the journey to the outer world? Now that I could think somewhat clearly in my mania, no one ever saw
someone leave for their journey.

Then the worst thought of all crossed my mind and all other thoughts fell silent. \textit{Was she
going to steal me away in the night and devour me?} From that moment on, all other thoughts were
mute and the gruesome details of this one fed one another. Coiling in on themselves, the thoughts
slithered into greater and greater clarity. I feared that, should I fall asleep, I would awake with
those tensile fingers about my throat and abdomen, fixing me in place as her jaws unhinge in
anticipation of evisceration to drip my entrails down her wretched gullet.

The swirling madness of my thoughts culminated in cognitive overload and cold sleep overtook me.

\noindent\rule{\textwidth}{1pt}

The sickeningly sweet aroma of rotting flesh was first to berate my senses. Opening my eyes,
expected to make haste to kitchen to discard my untouched dinner, but instead I beheld my room
without roof and a brown sky, akin to dried blood, overhead.

\vspace{5mm}
\textbf{Where was I?}
\vspace{5mm}

Standing up from the the half deteriorated mess that resembled my bed, my feet met the source of the
stench: soft, white, half-rotten flesh. I didn't dare look closer for fear of discovering its
origin.

Leaving the dilapidated shack that had uncanny semblance to my own home, I perceived a great waste
of puss covered ground and the same wounded sky above. In the vicinity were other equally broken
down houses that I recognized: Laurence Jeswalop, Adelade Farmer, and the now orphaned boys of
Zachary Edison. In the distance, I did see what appeared to be cruel abominations of anthropomorphic
proportions. Fearing my situation, any fate was better than staying still, so I made my way toward
the cliffs to confront the daemons.

Despite the entities only appearing about six or so miles hence, my pace was disproportionately
slow. Many times, I had to stop to wretch upon the pustulent ground, though my gut had nothing to
give, so my diaphragm would succumbed to fits. In some places, the sensation of the white mass
protruding up betwixt my toes caused me to stop and shudder violently, once badly enough that I
nearly lost my balance. I could tell that I was badly dehydrated as after my fourth mental break, my
tears no longer wet my cheeks and sharp sensations began to accost my kidneys. But possibly worst of
all were the thoughts within my ragged mind.

First and foremost, where was I? Why was everything red and white? Why me? Why am I naked? Is
Jennifer okay? Did lady Yağmur eat me and I am in hell? Is this the outer world?

\vspace{5mm}
\textbf{Is \textit{this} the outer world?}
\vspace{5mm}

The last question rang incessantly in the dishevelled husk that was my mind hour after hour.

During my travel very little changed save the time of, what I can only call, day. The dark
brown sky grew in luminosity until it reached a fevered red. Also, in the sky, to my horror, the
mockery of a Sun bore the same color as the blood from lady Yağmur's lips during the Libation, and
unfortunately, it rose in the sky in the very direction my defeated corpse was taking me.

\noindent\rule{\textwidth}{1pt}

Reaching the cliffs, my feet were beginning to swell from immersion foot syndrome and my skin was
clammy with the stink of rot, but I could now clearly see the humanoid beasts which I had spied
earlier. How long had I been walking? Long enough for the sanguineous sun to begin to set.

Gazing upon the forms that had beckoned me, I saw that I was at the fishing cliff and all about the
cliff itself were countless bodies hunkered over staring down into the water. Coming closer,
however, I found they were not staring into the water, but their necks had delaced themselves. Skin,
sinew, muscle, and vertebrae connecting and gripping to one another in a contorted mess creating a
line stretching down deep into the blackened waters below, upon the end of which, the individual's
head created a ten pound sinker. Every now and then, the bones, muscle, and tendons would contract
and convulse, bringing the head back to the top of the cliffside and a fish within its maw.

Gazing on, I could no longer comprehend what I saw, for my mind no longer was, so I continued to
watch as these daemons continued in their labor, until many of them began standing. Their necks, did
not fully retract as the skin did not reattach and muscle and bone did not realign naturally.
Instead, some of the more full bodies left their heads hanging to one side, while the more starved
bodies carried their heads in their hands.

After a few that had fish within their posession stood, a most languid procession formed, walking
past me. As I looked on, I began recognizing faces. William walked past with a fish, but body more
skin and bone than muscle in stark contrast to how I remembered him. His ribs seemed to try to rub
through the leathery hide that was his skin. Then, further on, I saw Zachary. Oh, Gods, Zachary. To
see you in such a state, vertebrae cracking and neck muscles squirming as you walked past, I now
know why you had not taken your boys; there was no choice and there is no escape.

With nothing else, I followed Zachary, for he was my friend in Gransford; here, though, he made no
motion or word to make sign that he noticed me. Following this poor case that was my friend, I
beheld a tree in the distance, the ash tree.

Immediately, energy seized my body and some hope reinvigorated my soul. Rushing best I could, I
clambered through the muck and filth, to that point that had been haven in days past. As I drew
closer, I saw a faintly glowing mass beneath the tree which halted my progression abruptly. After
capturing what little composure I had left, I edged my way toward the tree. There, I found what I
knew to be my mother. In this putrid place, the innocent, flawless being from my youth, my mother,
Isla, sat beneath the tree, gut bulging to inhuman proportions with her medallion wrenched into her
forehead, staring at the sky. With eyes trying to give any sign of liquid, I moved in closer, and I
could hear her muttering something. I did not understand and did not care, but simultaneously could
not bring myself speak back or to embrace this tormented apparition of my mother.

Now, glancing down the coastline, I could see many glows along the costline against the bloody sun
now defiling the horizon, and knew they were other souls akin to my mother.

I could go no where else. All else was naught. \textit{All} was naught. I could do nothing to save
my mother nor myself from this loathsome place. So there, I sat.

But not long thereafter, I felt something softly hit the back of my head during my mourning. Tiredly
motioning my eyes upward, I saw little white bits falling from the sky. I recognized what they were:
they were fish entrails. From the abhorrent sky, fish intestines and swim bladders were raining down
on all, as far as the eye could see.

Glancing over at my mother, she had not changed position, but was speaking louder as the bits of
fish rained down on her. Looking closer, I could see that the pieces were wriggling and moving upon
her skin, and then burrowed in, leaving no sign save movement beneath. Many on her face moved their
way toward her eyes and made haven there.

In horror I brushed as many as I could from myself, but noticed that many were already tunnelling
into my body and before too long, I could hear what my mother was saying:

\vspace{5mm}
% I partake and so I see. Thus I now feed.
\textit{``Katılıyorum ve bu yüzden görüyorum. Böylece şimdi besleniyorum.''}
\vspace{5mm}

Kneeling into the soft ground, Zachary makes his way over to me and stands above me. Opening my
mouth, I accept the fish that he offers and devour it in whole. \textit{Katılırım}. Fish bits
continue to make way into all of my eyes. \textit{ve bu yüzden görüyorum}.

Medallion now in hand, I raise it up. Looking into the sky, I see their forms, present, beautiful,
and gaudy in appearance. Through the din of the rainfall, I hear \textit{her} voice laughing
approvingly. With that, I know I have been faithful, so I press it into my forehead. Feeling the
soft flesh give and the bone make way, it fits perfectly as I begin to glow. \textit{Böylece şimdi
besleniyorum}.
