\chapter*{Denial}
%! he's finally old enough to talk to his mother about his abilities and see what the ramifications are, but he doesn't want them

\storydate{7: January 14, 1998}

``Hey, I'm here.''

Everything was dark and fuzzy. Rather, his mind was fuzzy. He could, however, feel something constricted around his left hand.

``Take your time. You're going to feel foggy for a bit, okay?''

The voice sounded muddled, dry, and distant. He tried opening his eyes to see who it was, but they felt swollen. Instead, he rolled around a bit. The constriction around his hand lifted, pulling him into an upright position.

\textit{Thank goodness mom's here. I must have passed out again.}

Once he was sitting up, he felt his mom scratching his back. It sent tingles up his spine, enough to make him shiver. Finally, one eye peaked open and the other followed suit. The room was dimly lit and quiet. Glancing around, he saw the silhouette of his mother sitting next to him on the bed. Everything was familiar: multiple pictures of Mario on the muted green walls, a little TV on the floor with the N64 next to it. One thing that was a little strange was that the room was clean.

\textit{Where are my drawings and colored pencils? Mom probably knows.}

He looked back at his mom. She looked tired but happy. Her brunet hair was in a ponytail today which accented her already tired, stretched eyes.

``Kory? Do you want something to eat?''

``Colored pencils. Where are my colored pencils?''

``I don't think you'll want to eat your colored pencils. I put them away, but we can color after you've eaten. What would you like?''

``Uh, waffles?'' His words felt sticky as he pushed them from his mouth.

``Sure, little king. Do you need anything else? You should probably try getting up, going to the bathroom, and washing your face. Take your time though. You were out for a bit this time.''

``Really? Oh, okay.''

She stood up and left the room, but her hand caressed the door frame as she glanced a weary smile back in his direction.

He still felt quite foggy, but more alert than he was just a few minutes prior.

\textit{What should I draw later? A robot? That's fighting the moon? Yeah! And the moon has a laser sword with...}

Kory clutched his head softly as it began throbbing. Now he noticed that his throat was pretty sore too. Luckily, on the bedside table was a glass of water.

\textit{Man, mom's the best.}

Drinking the water felt sharp as it made its way down, but it made his stomach feel cool. Still quite tired, he laid back down and closed his eyes again listening to the clatter of cooking from the kitchen. Sensation was making its way back to the rest of his body; his hands felt little needles and now he could wiggle his toes. Waking up from these fainting spells were tedious, but at least they didn't scare him anymore. One thing that came sooner than he wanted was the sensation to go to the bathroom.

Hopping out of bed, he found that his legs weren't as stable as he thought and stumbled sideways into his night stand, spilling the mostly full glass. Before he could replant himself, his mother came rushing in to help.

``Are you okay?'' she asked with a mild panic on her face.

``I still have rubber legs.''

She forced a small smile and giggled with him. Once she could see that he was stable, she reaffirmed that he was okay and let him go to do what he needed. As he left the room, he looked back and found her on the floor cleaning up the water that he spilled with her apron. In that moment, she seemed very old, though he knew that couldn't be right.

\line

Their modest kitchen swirled with the magical aromas of bacon and warm syrup as Kory found his way to the table. From the kitchen, his mother asked, ``How many waffles would you like? One or two?''

``Two? Cut up please?''

``Of course. You are my little King after all!''

He watched his mom pull one waffle from the iron and then another from a nearby plate onto the cutting board. There she used her magical knife skills to turn the circular waffles into square pieces. Kory had tried cutting his own waffles on numerous occasions, but they were nowhere near as good as his mom's, so he was content to let her do it for him. Maybe someday when he's bigger he'll be able to do things like her.

With two plates in hand, she made her way to the table and placed and returned to the kitchen for the orange juice and her coffee. As she sat down, he could see the biggest smile on her face. He knew that she was the happiest person in the world because she was always so cheery and positive, even when she was visibly tired.

Looking at his plate, he could see the two waffles cut up as requested, but the were mostly shoved off to one side. The majority of the plate was covered in bacon.

``Eat up, kiddo. I know you love bacon, so don't be shy.''

He moved his attention to his mother's plate.

``Mom, why don't you have any waffles? Do you want some of mine?''

``Oh no, honey. Silly me forgot to go grocery shopping, so we had less stuff than I thought. You go ahead and eat. I'm not that hungry.''

Placated, he returned his attention to his own plate and began eating.

For a while, there was just silence as he ate and his mother watched, occasionally sipping her coffee, until the grandfather clock in their house chimed. Kory loved to count along with the strums to find out the time.

\textit{One, two, three, four, five, six, seven, eight, nine. No more? Nine in the morning I guess.}

He looked up from his plate that was nearly empty at this point and realized that he probably ate too much. His mother was still watching him with a weary smirk that somehow confused him.

``What are we doing today? Are we going to learn some more about the culolonimus clouds and rain? We didn't finish that lesson last week.''

His mom sat up in her chair and processed what she just heard. He clearly forgot about coloring already, but she remembered that she had things to do too.

``It's cumulonimbus, silly goose,'' she corrected slowly, ``but you actually reminded me of someone that I need to call. They wanted to talk to you.''

She stood up and walked to the phone in the kitchen and dialed from a paper she had stashed nearby. He couldn't really hear the conversation, other than the stray sentence or phrase like ``yeah, he's awake,'' and ``when do you think you'll have an opening?''

\textit{What do they want to talk about? I guess I do know a lot about pretty much everything.}

Kory was trying desperately to find room to fit his last two slices of bacon in his stomach when his mom walked back in.

``So, honey, I have some questions that are going to seem kind of weird.''

``I like weird!''

``Different kind of weird, little king. Do you remember what we were doing before you passed out this time?''

``Not really. I think we were studying. Was it English? Those adjective things are hard.''

``I think we were doing social studies that day, but no, you were out in the backyard playing.''

``Okay?'' he said hesitantly.

``Do you remember what yesterday's date was?''

``Thursday!''

She gave a half-hearted chuckle. ``No, silly. Like month, day, and year.''

He thought for a minute. ``October 14th? 1996?''

``Okay. So I was just on the phone with a nice lady named Dr. Hall. She's an abilities counselor.''

``Oh, didn't Paul from down the street go and talk to one of those last year?''

``He did. You have a very good memory! I didn't even remember that he and his dad went to see someone. I've been meaning for you to go for a while, but I know that these kinds of doctors can be kind of hard to understand so I wanted to wait until you a little older. Luckily Dr. Hall is very accommodating. She said to call when you woke up and that she'd make time for you.''

``What's she like?''

``She said that she has a thirty-minute slot open in the afternoon, so we can meet her together and find out what she's like.''

``Oh. Okay. So we're not going to play or study today?''

``I don't think so. You just take it easy and have some fun before we go.''

Kory didn't really understand what was going on, but he did realize he had room for the rest of his bacon now.

\line

Kory hated sitting in waiting rooms. They felt too open and clean. The exam rooms were better as the walls were closer. Something about the disarray of chairs and magazines made him uneasy. He clenched his mom's hand and closed his eyes.

``Korinth Jacobsen?'' asked a nicely dressed lady standing in the opening of a short hallway.

``That's us,'' whispered his mother as she stood up.

The two of them made their way over, all the while the woman watched with a warm smile. Kory looked up at the strange woman. She was wearing purple horn rimmed glasses.

\textit{Those are funny glasses.}

``Is it okay if I come in or are these usually done one on one?'' his mother inquired as soon as they were within polite talking distance.

``You're free to come in if he wants it. Otherwise, you can wait out here. It shouldn't take long. As I said on the phone, these meetings usually only take about thirty minutes.''

Kory's mother knelt down next to him and held his shoulders. ``Would you like me to come in with you? You're just going to talk to Dr. Hall here for a little bit.''

He didn't really know what was going on but having his mother nearby always made him feel more at ease. ``Will you come in?''

``Of course. I'm always here for you.''

``Wonderful! Follow me back to my office,'' urged Dr. Hall.

With that, they all headed down the hall and entered a room at the end on the left. The inside of the room was nothing like what Kory expected. He thought they were going to see a doctor.

\textit{Where's the exam chair with the paper? Why is there carpet in here? Why are there pictures of papers with writing on them rather than the cool posters about the brain and stuff?}

Kory was so distracted that he didn't hear Dr. Hall invite him to sit and kept gawking at the room.

\textit{There are plants in here! They're growing all over. Look at that one. Its vines are growing up and around the window! Do you think she has dirt in h...}

Suddenly he was pulled from his stupor by his mother's hand on his shoulder.

``Kory, sit down please,'' she said as she patted the leather love seat where she was sitting.

Once he was settled, Dr. Hall began.

``So, Korinth, would you prefer I call you Kory like your mom, or something else?''

``Kory is good. I like Kory. It's easier to spell than Korinth.''

``I'd have to agree with you on that one. And how old are you, Kory?''

``I'm seven, almost eight!''

''Congrats! Eight is when you become the man of the house, isn't it?''

That seemed like a weird statement. He was the man of the house as dad wasn't around.

Dr. Hall noticed him make a bit of a funny face at the retort and brushed it off with a small shake of her head. ``Do you know why you're here or what I do?''

``I know that one of our neighbors came to visit someone like you, right mom?''

His mom gave an approving nod before he returned his attention to the doctor.

``Good. Well, let me try to explain a little more about what I do. I'm what you call an abilities counselor. As you may or may not know, there are many people that have powers that are kind of like superpowers from your comics and TV shows! Usually these powers are nowhere near as powerful and tend to be a problem for people rather than making them Superman.''

``But I thought you were a doctor? Do superheroes need doctors?'' Kory was a bit overwhelmed with this doctor not needing to taking his temperature and growing plants all around the room.

``I'm a different kind of doctor. Not a medical doctor. I talk to people and try to help them cope with their abilities and find normalcy in the day to day. Does that make sense?''

``I think so. So, you're like Batman's butler who helps Bruce Wayne do all his normal things while he goes out and beats up the bad guys?''

``Almost. I help people be comfortable with their powers.''

``I see. But I don't have any powers. Are you going to give me some? I want spider webs like Peter Parker!''

``I can't give you powers. Honestly, the latest research doesn't even know why or how some people have them in the first place!''

Dr. Hall made strange eye contact with Kory's mom as if to ask something to which his mom provided a small confused shrug.

``Kory. Your mom called us a while back asking us to meet you because we're pretty sure that you \textit{do} have an ability.''

The thought of having an ability gave Kory chills up his back.

\textit{What could my power be? It has to be something cool. Laser eyes? Am I super strong? Can I walk on walls?}

The counselor smirked a bit as she could see the flurry in his mind, but pulled him back to reality.

``Kory. Your mom told us about your symptoms, which I want to confirm with you, but we're fairly certain that you have body/self dissociation.''

\textit{I have what?}

``I can see that you're confused, and to be honest, it's one of the more confusing abilities that's out there. Let me start by asking you some questions and try to help you connect some dots. Do you know what today's date is?''

\textit{Again with this question? Why are adults so fascinated by the date and the weather?}

``Uh, my mom already asked me this earlier. It's October 14th. 1996.''

Dr. Hall nodded. ``Has your mother told you what today's actual date is?''

``Why would she?'' replied Kory as concern crept into his countenance.

``Kory. Today is January 14th 1998.''

The silence hung like the plants over Dr. Hall's windows. Kory looked down at his hands and started counting.

``You mean I've been asleep for fifteen months? My superpower is sleeping?''

Dr. Hall's eyes beamed as she pushed the purple glasses up her nose.

``Actually, you're not sleeping! This is where it actually gets really fascinating! In the case for normal people, when they go to sleep, their body continues to metabolize and their brain function continues. This is even largely true for people in comas. For people like you, which coincidentally are few, your body doesn't seem to metabolize and there's zero brain activity! There are a number of theories but most of them stem from Descartes, Leibniz, and Spinoza. In their works they rationalized that there is a distinction between the self and the body. In most cases, the line is quite blurred. It can also be dangerous in some cases such as depressive dissociation, where the person believes that they are experiencing their own life as a third party observer. An out-of-body experience, if you will.''

\textit{None of this makes sense. How could I just not have fifteen months? Where did they go? I was awake yesterday. I had breakfast. I played in my room. I did my homework. Yesterday. It was all yesterday.}

Dr. Hall continued. ``For you, however, there seems to be an additional level of dissociation! As I said, the current theories are that the self and the body actually disconnect for some undetermined amount of time. During that time, the body enters a stasis of sorts and ceases all function, but oddly enough retains warmth and a few other traits that indicate that the individual isn't dead.''

``Doctor!'' interjected his mom, though it did little to wake the doctor from her frenzied excitement.

``The question is, what happens to the self during this time? Where is it? Is it tangible? These are some of the fundamental questions that still haven't been answered by philosophers \textit{or} physicists. What is understood, however, is that the individual doesn't seem to know either and wakes up when the two reunite, seemingly with no break in their understanding of time, despite considerable time passing. It's almost like time travelling!''

\textit{So I can time travel?}

Kory glanced over at his mother to get some affirmation of what he should be feeling. She looked angry, but he wasn't sure why. He didn't really want to be there anymore either as this lady was weird and scary.

``Dr. Hall. Are you a counselor or an academic?''

``Actually, I'm both! I would love to continue studying your son as this ability is quite rare. When he has another episode, call us and we can bring all the equipment to your home and figure out what's going on! Then, when he wakes up, we can get him on a regimen of sessions and medications and see where that takes us, but this is all very exciting stuff. Wouldn't you agree, Kory?'' She stared big eyed at Kory like he was a meal.

Kory's mom put her arm around him and pulled him in close.

When he didn't respond, she continued, ``In the meantime, we could set up some sort of...''

His mom cut her off. ``No, I don't want my son poked and prodded when he's so vulnerable.''

``Oh please. When they're having an episode, they're hardly even human.''

\textit{What? Now I'm not human?}

Kory felt tears start to well in his eyes as his mother shot up. He had never seen his mother like this. She turned and grabbed his hand. ``Let's go, honey. Dr. Hall isn't really interested in helping. She just wants to publish another paper.''

Confused, Dr. Hall timidly raised her arms as if to beg for reconsideration.

\textit{Paper? Time travelling, I'm not human, and now paper? What's going on?}

Wiping the tears that began rolling down his face, the two of them started for the door.

``Mrs. Jacobsen. Please think about it and call me. I won't charge for today's meeting. As for you, Kory, it was a pleasure meeting you!''
