\chapter*{Anger}
%! Kory's angry that he has to time skip and refuses to do so and skips uncontrollably

\storydate{10: April 16, 2008}

``Hey, Kiddo. I'm here.''

\textit{Another blackout. I hate these. Wonder how long I was out this time.}

He ran through his current options.

\textit{I haven't moved yet, so mom probably doesn't know I've woken up yet. She's probably just talking to try to get me to wake up. I could just lie here and pretend to be asleep. That certainly seems like a better option to waking up and pretending that this is no big deal.}

With his mind made up, he stayed in bed, unmoving.

``You know, as your mom, I do know a thing or two.''

\textit{What do you know? Do you have to put up with this stupid ``ability''?}

``Like, for instance, I know that when you're time travelling or in stasis or whatever we're going to call it, you don't breathe. Why don't you get up and talk to me? I have a surprise lined up for you.''

He mulled his new options around for a bit. After thinking for a bit, he decided to hold his breath.

``You goose! You can't fool me!'' she exclaimed as she pounced and began tickling him.

Impulse swept in and his abs contracted, shooting his legs into the air. Gasping for air, he pleaded for her to stop.

Once she stopped, he looked over at her. She had a wide, warm smile on. Her hair was in a braid today which showed her ears, but also accentuated a bandaid on her forehead.

\textit{Mom must have hit her head one something.}

All of a sudden, he remembered that he was grumpy and that he didn't like being happy. The smile on his face disappeared and his brows furrowed.

``Oh come on. What's wrong?''

He continued to pout for a minute, but soon started to feel the pangs of waking. His head began pounding and needles radiated through his limbs. He didn't want his mom to watch him while he took a moment in the fetal position.

``Hey, mom. Do you think that we could have pancakes?'' he asked in attempt to get his mom to leave the room.

``Sure, king, but you probably haven't noticed that it's eight pm.''

He turned as best he could and glanced out the window. Outside his window, he could see his dogwood in bloom and behind it, sure enough, were the stars.

``I want pancakes.''

He couldn't think of much else as he wanted her out, but didn't want to hurt her feelings.

``Okay, okay. I'll go start making some pancakes. Would you like some bacon with that too?''

He stammered a bit. ``Ye... yes please.''

She got up from the bed slowly as the smile faded from her face.

\textit{I'm not sure how long I was out this time, but I'm sure that she has no idea how I feel. Waking up is terrible. Everything hur...}

He stopped mid thought as a stabbing pain pierced his chest. Curling up on his bed helped the pain a bit and after a few seconds, it abated. Clutching his chest, he sat back up on his bed to finally take a look around. Sure enough, not much had changed. The walls were still a forest green color, most of the Mario posters were taken down, and a desk sat in the corner with various magazines and papers strewn about.

\textit{I hate this ability. Why do I have to have it! It's ruining everything! I didn't even know what time it was!}

He noticed that his fists were clenched and teeth grit, so he tried taking some deep breaths, though that proved more difficult than not. The air seemed sharp as he expanded his lungs and air he expelled felt stale. He glanced over at his desk again. Nothing seemed to have moved on his desk, even though the rest of the room was clearly cleaned. Without second thought, he stood up and walked over to the chair and sat to examine his desktop.

Surely enough, everything was right where it would have been had he only been asleep for the night. Right on top were the envelopes and hand drawn invitations that he had been working on.

\textit{I don't even get to have a birthday.}

The thought caused tears to well up in his eyes. Looking back down, he blinked hard, and two tears made their way down his little cheeks.

``Hey, little king. Your pancakes are ready. Are you feeling okay?'' The soft touch of her hand on his hair made him jump a little.

Quickly he ran his arm across his face to remove his fresh tears. ``I'm fine,'' he retorted as he stood up to leave the room.

At the table, he found a plate with a stack of three pancakes. Scattered throughout their surface were little blackish blotches. He couldn't tell if they were chocolate chips or blueberries until he got closer and sat down. They were chocolate chips. He probably would have lost it had they been blueberries.

His mom languidly made her way into the kitchen, poured herself a cup of coffee, and sat herself adjacent.

``Hey, Kory. I know that you're having a tough time, but you know, we'll figure out this ability stuff together.''

He didn't want to listen, but unfortunately the food was in the same room as her. In protest, he tried using his utensils loudly, but within reasonable noise levels. Aside from the clanking of his fork on the plate, they sat in silence until he was done.

Her gaze scarcely broke from him and he could feel it. It moved around from his hair to his feet. She was inspecting him. Slowly.

``Kory, I...''

``What do you know about these stupid abilities! What do you know about how we're going to work through this? What if I don't want to work through this? I just want to be normal! I want to go to school with other kids, not homeschooled. I want to know that tomorrow is going to be tomorrow and not two years from now. I want to wake up and not feel like I'm dying. I want to have a birthday party!''

The last point broke him and he began to weep.

``How long was I asleep this time, mom?'' The question was forced through tears, snot, and gasps.

Shocked, she took a moment to realize what had just happened.

``Kory,'' she said even more softly than before and wrapping her arms around his shoulders, ``I'm sorry that this is hard and that I can't take it away. Please know that I'm trying and that I'll do anything for you.''

He laid his head into her shoulder. A few strands of hair pulled from her braid and fell on his face. It was warm and he knew he was safe. Her breathing was slow and labored like she hadn't slept the night before, but there they stayed a moment.

Words kept spilling out of his mouth as his brain tried to conjure something to say, but his thoughts were incoherent.

``Shhh...'' she whispered. ``Do you remember that I said I have a surprise lined up for you earlier? I think it's better that I don't keep it too much a surprise.''

He perked up at the thought.

\textit{What did she get me?}

``I called a bunch of people that I know that have kids around your age, and I invited them to come over for a birthday party for you.''

He picked his head up and glanced at her with questioning eyes, but she responded with a frail smile and crescent eyes.

Suddenly she perked up. ``You know, it's pretty hard to plan birthdays for you, but we'll always make the best of it!''

His mood dissipated at her joke and he returned to his cheerful self. ``When is it going to be?''

``This Saturday at eleven o'clock.''

The thought energized his brain.

\textit{Should I finish the birthday invites? How many kids are coming? What presents are they going to bring? What are we going to play? It's going to be at eleven o'clock? That means we'll probably eat lunch too! What are we going to eat? I hope we have bacon.}

``Can we have bacon?''

``What?''

``At the party?''

``Sure,'' she chuckled, ``anything for my king.''

``What date should I write on the invitations? Did you see the ones that I was making on my desk?''

``I did see them! They are very good. You should write `Saturday, April 19, 2008' on them.''

He could tell that a weight had been taken off his mom, but he couldn't help hearing that the year was 2008.

\line

\storydate{10: April 19, 2008}

Kory found himself peering out his window, watching the strange kids gather in his backyard as they arrived one by one. He found himself thinking about how he had never really been around other kids and that this was his first birthday party.

It felt like just a few days ago when his mom told him that he could have a party, and so he started making invites. He didn't know who they were for, but he was certain that he would be able to make friends with some kids around the neighborhood that he had seen on occasion.

Then he skipped. He didn't like calling it that, but he and his mom had agreed that it was probably the easiest thing to call it.

\textit{Skipping is such a dumb word for it. Makes it sound like I'm doing it on purpose. Why would I do this on purpose? That's stupid. I hate it. I hate it.}

He could barely see out the window now as his brooding caused him to slouch deeper into the window sill. Despite only seeing half of his yard now, he could see one kid that seemed off. Nothing was out of the ordinary, other than his bubbly demeanor and the strange gloves that he was wearing.

``Hey, little king. You ready to come outside? People are waiting to see the birthday boy!'' Her kind smile emanated into the room, but fell short of cheering him up. He knew it was a special day, but somehow he didn't want it. Somehow he wanted to be left alone.

``I guess.''

He tried protesting quietly by dragging his feet as he walked. Despite his silent petitions, they made it to the backyard. There, he could see clearly how many kids there were.

\textit{One, two, three, four... seven kids total. There's the kid with the smiles and gloves. They all look so happy.}

It seemed so odd that they were all happy. He wasn't really sure what to expect, taking a few steps into his own yard.

\textit{Are they all going to turn and acknowledge me? Stare at me? Do they know anything about me? Do they know each other? What are we going to do? Maybe I can just hide somewhere.}

Just a few days ago he was so excited about his party, but now he wasn't so sure. He was certain that he was out of his element and that he wasn't sure what he was supposed to do.

Sensing his unease, his mom placed a hand on the back of his head. ``How about you go and introduce yourself to the other kids.''

He shot a distressed glance at his mother, but he knew that he would have to talk to them sooner or later. Walking the ten paces to them seemed to take an eternity, but eternity was over in the blink of an eye. He found himself standing behind their circle, listening to their conversation.

``Look what I can do!'' said one of the boys as he tried holding a hand stand, but quickly fell over.

``I can totally do better than that.''

``I bet you can't!''

``Anyone could do better than that. You didn't even get your feet in the air.''

``Well, my dad can do that for a whole hour!''

The fighting continued for a moment and then one of the boys bumped into Kory.

``Oh, hi there.'' said the helplessly cheery boy with the gloves. Looking around, Kory noticed that there was something strange about all the kids there.

Kory opened his mouth in an attempt to introduce himself, but hardly a breath came out.

``I'm Jacob!''

``I'm Peter.''

One by one, the kids all introduced themselves save the cheery one.

``And I'm Carl! It's nice to meet you! Do you want to play? What's your name?''

Kory, squeezing his eyes shut and taking a deep breath, he finally managed a meager introduction.

``I'm Kory. What's with your gloves?''

Taken aback, Carl tilted his head slightly, but without skipping a beat replied, ``Oh, these gloves? They're special gloves to hold the bones in my hands in place. I have an ability where the bones in my hands don't stay in place and my skin is super stretchy! It's kinda cool, but I can only really do anything as long as I'm wearing these.''

``What's your ability called again?'' jeered Peter.

``It's localized hyper-elasticity.''

``Localized hyper wiper...'' Peter trailed off into jabbersville, waving his hands high in the air, slowly waddling away.

``We all call him rubber band hands.'' said Julio over Peter's nonsense.

Kory glanced over at Carl who returned a wry smirk.

``I can show you if you want. It doesn't hurt.''

Kory was curious, but could only manage a weak nod. With that, Carl began taking his gloves off, which seemed to be quite the task.

First he had to let out the pressure by turning a small knob on the wrist and then each finger had to be unsplinted. Watching him do this, Kory was glad that he didn't have to wear something like this.

When Carl finished undoing the glove, he took it off and immediately all of his fingers stretched to the ground and bulged like little sacks of water.

The other kids watched and giggled all while chanting ``rubber band hands.''

Carl looked up into Kory's face to see his reaction. Kory wasn't sure what he was looking, but couldn't tear his eyes away.

``Yeah, well that's a silly ability. Mine is way cooler!'' chimed Mary.

\textit{Cool? This is cool? She has something cooler?}

Kory jaggedly recentered his gaze on Mary.

``I can put thoughts in your head!''

\textit{She can put thoughts in my... poop.}

``Poop?'' questioned Kory.

``Poop!'' she replied between laughs. ``I put poop in your head!''

``Mary! What have we said about putting thoughts in peoples' heads without their permission? Especially poop.'' chided a parent from the other side of the yard.

``Sorry, dad.'' Looking back at Kory, she asked, ``But that was funny, right?''

He just continued looking at her with a blank stare.

``Hey kids, come get some food! After, we're going to do the piñata.''

All the kids got very excited and ran over to the food table, all except Carl who was still trying to put his hand back into his glove.

``Carl! Why'd you take your glove off?''

``I was showing the quiet kid!''

``Goodness, you know it takes like five minutes to put these gloves back on...''

Kory, turned his attention toward the food table. There he saw hamburgers, hot dogs, and bacon. Suddenly he wasn't so shy and ran over to the table to grab a few strips.

``What do you think of the other kids?''

With a mouth full of bacon, he spun around to find his mother.

``They're... nice?'' Kory gave a confused grimace. More than any other time in his life, he realized that he didn't know anything about other kids. ``Mom? What's a piñata?''

``Oh, right, we've never had a piñata before, have we? Well, you'll find out soon enough. I'm sure that the other kids will be more than happy to show you.''

He didn't like that answer. His consternation began welling up again, and with it, so did his frustration. To keep from losing control, he closed his eyes again and took a deep breath.

\textit{Breathe in. Breathe out. Breathe in. Breathe out. It's not helping. Hopefully everything starts turning out better. I don't want to scream in front of all these people.}

Looking back at his mom, he could see that she was concerned.

``Are you okay, Kory? If not, I can ask everyone to go home.''

``No. I'll be fine. I want to make friends.''

Her countenance softened. ``Okay. I'm glad. You seemed to be hitting it off pretty well with that one boy, the one with the gloves?''

``Carl?''

``Yes, I believe that's his name. His mother is quite the doll as well. Why don't you try to get to know him better too? I see that he's over eating with his mom right now.''

He gave a half-hearted nod and shuffled over to where Carl was sitting.

``Hey! Kory! You want to sit down?'' Carl's smile was so big that Kory thought his face was going to snap off at his ears.

``Yeah...''

``So I heard that you have an ability too! What is it? Is it something cool?''

``Where did you hear that?''

``Our moms were talking and your mom told my mom that you have an ability, but said that we should talk to you about it. I love surprises! What is it?''

``I... I don't really want to talk about it.'' Carl's mother nudged him hard enough that he rocked in his chair.

Seemingly unaware of the reason for his mother's prodding, he continued. ``Aww. How come? I mean, I didn't really like my ability either for the longest time. But then we started going to an abilities counselor and she's been great!''

``An abilities counselor? You like your counselor?''

The sound of the other kids playing in the background was so loud and annoying. Kory felt his head start pounding.

``Yeah, she's the best.''

``Dr. Hall! She's got these really cool plants in her office. She said that she got them from Brazil when she was studying some really weird abilities that only happen in that part of the world!''

\textit{Dr. Hall? The lady with the weird glasses? The lady that said I wasn't human? That Dr. Hall?}

Carl was still rambling about something, but Kory tuned him out and looked at the other kids more closely. He saw that Julio was levitating about two inches off the ground before face planting whilst his onlookers laughed along with him. Mary was staring intently at another boy and giggling; probably filling his head with poop.

\textit{I bet all the kids here have some kind of ability. Was this mom's plan? Was she throwing this party for me to be a normal kid, or was she throwing it to put me in with all these freaks?}

``What do you guys know about my ability? It's not funny! It's not fun! I don't want it!'' shouted Kory as he stood up, pushing his chair over.

``You think that I like skipping? You think that basically disappearing for who knows how long every year and waking up thinking that it's just been another day?

``You think that I don't want to make friends, but know that I won't know where or who they are the next day because it's been two years?''

The party had broken into utter silence with all eyes plastered on him.

``All of you here playing around with your abilities thinking that they're just little things that are funny, that they're just little tricks that are cool to show people! Well guess what? We're basically not even human!

``Yeah, you, knuckle dragger! And you, poopy brain!''

At that point his mom had made it over to him and grabbed his hand. He looked up with teary eyes and saw that she had tears in her eyes. He looked back at the yard. A number of kids were crying, particularly Mary, and all the parents looked mortified.

``I'm sorry everyone, but the party is over. Please help yourself to any of the food and cake on your way out, but I need to help my son.''

Kory's mom, firm handed, led the way back into the house and to his room. There, she let out a palpable sigh.

``Kory. I know that life is hard for you and that skipping seemingly ruins everything. Trust me, I know, first-hand. But that doesn't give you the right to be overtly rude to people that are trying to make friends.''

Kory sat on his bed and folded his arms. There he let the silence ooze into every corner of the room.

``Kiddo. I love you and I hope that you know that I'm trying my best to help you in any way that I can. You'll always be my eternal, little king.''

Through the silence, they could hear the party goers leaving and what they were saying.

``Can you believe she lets him do that?''

``I would never let you act like that.''

``Glad that's not my kid.''

His mom knelt down in front of him and clasped his hands. He thought it was weird that her hands were clammy.

``I don't care what they say. They don't know what you've been through,'' she said calmly. ``I do know. I want to know. Let me help you.''

Kory looked up at her and the tears running down her face, the unbreaking gaze into his eyes, and the messy bun that seemed to be coming undone.

``I'm sorry, mom.'' It was quiet, but it was sincere. ``I just hate my ability. I hate skipping. Why does everyone else get to live normal lives? Why do their weird... things get to only be an inconvenience?''

Her eye contact broke for a moment, but came right back. ``I don't know why we have abilities. But, I do know that it's what we have, so we need to try to be positive and do the best we can.''

The front door closed as the last of the other families made their way out.

``Let's try to be strategic about this, yeah? Do you know when you're going to skip? Do you feel funny?''

Kory took a moment to think about it while he wiped his nose on his arm.

``Yuck, kid.'' said his mom, reaching for a tissue to clean him up.

``I guess I do kind of know when it's going to happen. I start feeling weird.''

``What kind of weird? Is it distinguishable from other `weird'?''

``Yeah?... It's kind of like when you have to sneeze. But I feel it in my whole body. Like I'm all tensed up. But just a little? I don't know how to explain it.''

``No, no, that's good. Next time that you think you're going to skip, can you tell me? Let's try and do something about this.''

``Okay. You think I can hold it in? Like holding in a sneeze?''

She chuckled. ``Yeah, let's try and hold in your time sneeze.''

\line

\storydate{11: May 4, 2009}

``Hey, little king. How are you feeling today? Still feel the time skip sneeze coming on?''

``Yeah. This sucks.''

``I know. But you know what? The part right before the sneeze is always the worst when you're trying to hold it, right?''

``Yeah... but why is this going on for so long? It's been like a week!''

``How about we go to that diner downtown and get their pancakes and bacon for breakfast? You really like their food.''

Kory perked up a bit. ``Their bacon may be even better than yours!''

``Hey now! Say things like that and I may not make...''

Kory saw his vision close in and then felt like he was floating, until he hit the floor.
