\chapter*{Purpose}
%! only chapter from mother's point of view - waiting for her son to come out of stasis (where we learn what he's like during a time skip)
%! she's completely not taking care of herself as it is an undisclosed time into the future
%! learn that the mother has been dealing with the depression of knowing that living forever is not a blessing and will have to carry the heartbreak of getting close to others
%! reveal that the mother knows of, but does not know, the monster that stalks them
%! story ends with it speaking

% she recounts some happy times in her life, particularly concerning Kory's dad

\storydate{FILL IN DATE}

``Hey, kiddo. Just know, I'm still here.''

She sat by his bedside in the chair from his desk. The chair was worn from decades of use, but she couldn't find the time to tear herself away from his bedside to go get a new one, and the kitchen seemed so far away. What if he woke up while she wasn't there? What would happen then? She had always been there to greet him when he woke.

His face was still, soft, unmoving. How long had she been out before he had to skip? Even though it was clearly her son, she could sense his distress.

``You must have been so scared, little king. I'm sorry for putting you through that.''

She brought his hand up to her face and snuggled it against her cheek. It was warm, but it was no longer the hand of a little child. He had grown into a man.

\textit{When did my boy grow up? At least I was able to be part of all of it.}

Reminiscing on the times he was little, a small smile made its way to the corners of her mouth.

``I suppose now that you're a man, I owe you some answers. You asked a lot of hard questions when you were little.''

It was hard for her to think about the earlier years of her life. They seemed so distant.

``How about we start with your dad. You never knew him, but Tom loved you as much as any man was capable. That's right, his name was Tom; Thomas Jacobsen.

``He was an incredibly generous and soft-spoken man, which was quite strange back in that day.''

Looking at the corner of his room, like something was there, she tried remembering more details to impart.

``When was it that we met? It was... sometime in the late 1800s, I think. It was a very long time ago.''

She chuckled to herself. ``I suppose some things are easier to remember than others when they're that long ago.''

Thinking about her past, she shuddered at the simplest thought of some of her demons.

Shaking her head, she brought her attention back to her story and her son. ``Oh I remember, it was 1895. To that, I hear you ask, `1895!? There's no way that can be right!' To which, I tell you, I may look young, but I am certainly not. I've been around the block, not just a few times, but enough times to remember when the block had dinosaurs!''

\textit{What am I saying? Nonsensical rambling. Though, what else am I to do? I should keep talking to him in case he can hear me.}

``But, your dad, he was so handsome and young. When we met he was about twenty-three years old. I think we met at the local butcher shop. He was ordering what seemed like an entire cow.

``A wry comment from myself got his attention and we began talking. It turned out that he was a manager at the local malt liquor brewery and was buying some things to help out a few of the local families that had landed on hard times.

``That kind of generosity was unheard of back then. Largely, people were so cut-throat, trying to get ahead in any way that they could. The American Dream is all they wanted, granted, not nearly as much as when the Louisiana Purchase opened up. That's a story for another...''

She cut herself off before she promised a recount of that story. She clenched her stomach as if some wound there had never healed.

``Let's just say that people were blinded by all sorts of demons; ambitions and aspirations. And yes, your old mom was there for that too.'' Her body ached, her head pounded, and her feet felt cold.

\textit{Maybe I should turn on the heat... No, there's no sense in wasting energy. He doesn't respond to temperature when he's skipping. As long as it's comfortable when he wakes up. That's all that's important.}

She leaned back in the chair so she could get a look at the thermostat in the hallway.

\textit{Eighty-one degrees. Really? I must be running low today. When's the last time that I ate? Must be more than a week ago; I haven't moved from here in days.}

Returning her gaze to Kory, she peered at the freckles that were on his eyelids. They weren't visible when he was awake, but she loved looking at them while he skipped.

``I should continue my story about your dad, shouldn't I? I bet you're curious.

``Well, after the butcher shop encounter, we started bumping into each other more often. I'm pretty sure that he was secretly following me and `bumping' into me to have an excuse to talk.

``At length we started a beautiful courtship, though his mother wasn't the most lovely woman. She vehemently protested to Tom behind my back. It wasn't until much later in our marriage that Tom told me that she was deeply racist and didn't like me because she couldn't put her finger on where I was from. Naturally, that meant I wasn't English or French.

``Despite her protests, we were married. It was such a wonderful day; things couldn't have been more perfect. It was a clear Saturday; June 11, 1898. He wasn't a terribly large man, but he could command the attention of any space he entered. He stood about a half head taller than me and would envelop me with his soft eyes whenever we held each other.''

A longing sigh escaped her lips.

``Tom was my reason to continue. We were very happy together, and he adored me despite the visible trauma I carried. He continued being the loving, caring man that I had met at the butcher shop, except now he held me at the peak of his attention.

``Shortly after we were married, your dad became the owner of the brewery where he worked and life became a dream. Though he worked long hours, we wanted for nothing, save children.

``Luckily, we soon had that on the way as well. We found out in early 1901 that we were going to have a child.''

She took a moment to catch her breath as this much talking was exhausting what little energy she had.

``Of course, with any happy story, there comes a point where some unseen hand comes in to balance the scales. Nine months after we found out I was pregnant, you did not come, and so we waited.

``A few months later, we began to be very worried and went to see any specialist that promised to have an answer, though none could provide a suitable answer once they met us and our situation.

``Little seemed wrong, save the fact that you were taking so long to come into our lives. So, we patiently waited. Tom began cutting hours at the brewery so that he could be at home with me, should the time arrive.

``At long last, you decided to bless our lives on May 1, 1902. I believe that the pregnancy was about sixteen months, but you were perfect. Not a single thing wrong.

``Let's see,'' she said as she began doing some finger math with the hand that wasn't clasped around his. ``I think that would technically make you about... five hundred years old! Gee-whiz, that makes you an old man!''

She began to chuckle, but a stabbing pain in her chest stopped it short.

``You were such a blessing. A snotty, poopy, crying blessing, but a blessing nonetheless. Tom found every opportunity he could to hold you and to pamper you. Sometimes he went as far as to say you needed to be changed just so he could tear you away from me!

``However, the pendulum needed to swing back and with it, steal away our bliss. Just about a week after you came into our lives, you left; your first skip. At first, we thought you were sleeping, so we let you, but when you didn't wake up that evening, we panicked. You weren't breathing and were unresponsive to anything we did.''

Tears formed at the corner of her eyes, though she did not wipe them away.

``We rushed to any place that would see us at that hour, but that was few. Amidst the confusion and hurrying, you stayed warm and that gave us hope, so we continued our search all night and into the morning.

``At long last, a few hours from home, we found a doctor that would see us, but he told us that he had never heard of such a thing: a child in a perpetual, unbreathing sleep.

``When Tom and I had completely exhausted ourselves, we sat in a park and I told him that I believed you were alive. Despite it being a seemingly hopeless situation, I had a feeling that you would be okay.

``His soft green eyes sat deeply on my soul at that moment and he said, `Well, there's no doubting a mother's intuition,' and with that, we went home. What else could we do other than wait and trust that you were okay?''

With the back of her sweater sleeve, she removed the traces of tears from her face.

``To our surprise, you continued to stay warm, and so life continued on. I carried you around in my arms as much as I could and your dad carried you the rest of the time.

``In and out of years, you kept us waiting. Tom continued to build his business and reputation to the point that we were the wealthiest people for miles around. Despite his success, he always came home at the end of the day and would exuberantly declare `I'm here!' as he scooped you up in his arms.

``Slowly, but surely, just like all the other people in my life, Tom started to get old. He never gave up on you and believed that you would come back one day. Tom tried to be there for you when you woke, but in the end, he couldn't hold on anymore. It was November 23, 1943 when your dad passed away. He held on for fourty-one years. He believed, never wavering, for fourty-one years that you would wake up. That was such a hard day.''

She tried to repress her emotional scars, though it was futile.

``At his funeral, hundreds of people, extended family, work colleagues, business affiliates all arrived, though I knew next to none of them. We had largely kept to ourselves so that we could be there for you, so attending the viewing was like walking into a crowd of strangers.

``Given my appearance, many people assumed I was his daughter, holding his grandchild; not his wife. Person after person stabbed me as they expressed their condolences for my father.

``That night, I sobbed uncontrollably with you in my arms. The only thing that I could do was to continue to be there for you, as my reason to go on died that day, but my purpose lay in my arms.''

She extended her arm and stroked his hair. The sleek, unkempt hair ran through her dry hands. The sensation in her numbed hands caused her to wince.

``For the next twenty-seven years, I hardly moved or ate, curled up with you in our bedroom; nothing could disturb our living death.''

A slight ease came to her weary, green eyes, as she breathed and continued.

``It was June 4, 1970 when you finally woke up. I know because later that day I went outside to procure the paper. Your crying startled me so badly that I nearly dropped you. I held you close and cried, even though it hurt to move. The sound of your crying was music to my ears; it was a release from my personal hell that I never expected to escape.

``Words hardly do justice when I tell you I was stunned to see how the world had changed in all those years of waiting. The next few weeks were spent running around, trying to find ways to take care of you in this new world.

``I found that wet nurses were no longer a thing and that they now had milk banks. People no longer relied on the newspaper for their news; instead they used something completely foreign to me called radios.''

She looked over at all the electronics scattered about Kory's room and smirked at the irony.

``Even though Tom wasn't there to hold you, he's the one that is still carrying us both. In his lifetime, he became very successful and invested his fortune instead of living lavishly, as his business partners did. Tom had a plan: he was going to care for you one way or another.''

It had been a very long time since she had talked this much and she was parched.

\textit{Kory's not going to mind if I drink his water. I'll make sure I fill it up before long.}

Taking an enthusiastic gulp, she nearly coughed it up.

``Tom was an amazing man. \textit{Your dad} was an amazing man.'' She expelled a heavy breath. ``I'm sorry, Kory. All this talking has made me very tired. I'm just going to shut my eyes for a bit, but I want you to know, I'm here.''

\line

% she recounts some upsetting times in her life, particularly about her first husband

\storydate{FILL IN DATE}

``I'm here, Kory!'' she blurted as she jostled awake.

It was dark in the room. Even the light of the moon barely made it inside.

\textit{What time is it?}

She looked down at where her boy lied motionless. She could hardly see him in the faint light.

\textit{Seems that he still hasn't woken up. I should get up and get some light so I can talk to him.}

As she tried to stand from the worn chair, her knees creaked and her elbows were weak. Standing took significantly longer than she had anticipated, though she did eventually make it.

Slowly making her way to the closet in the hall, she procured a candle and some matches. She could have turned on the light, but she had always preferred candlelight to lightbulbs.

Again, she scrupulously made her way back to the room, watching where she placed her feet and trying to keep her balance.

\textit{The last thing that Kory needs when he wakes is to take care of me.}

Before she sat down, she attempted to light the candle, though she couldn't juggle the items in her once nimble hands. Little streaks of arthritic pain forced her to sit and place the items on his bedside table.

Once she had rubbed the pain away with her dry, cracked hands, she took up the candle again. This time she successfully lit it. The meager light it provided revealed an unkempt room. The posters that once hung on the walls were now on the floor and a film of dust covered everything.

She returned her attention to her son and to her shock, he was covered in dust too. Though labored, she pulled up her sweater sleeve and used it to wipe his hands and face.

\textit{There we go. I can clean everything else later, but you... you I'll keep perfect, little King.}

Sitting in the dull silence of the room, she could almost hear the faint whisper of the candle burning as it cast dancing shadows across Kory's face.

``How are you today?'' Her hoarse voice shocked her, but she needed to talk to him.

``You know, I like using candles when you're skipping. It saves on electricity. Why waste your father's hard-earned money? Also, I like the way that it lights your face. It makes it look like you're here and breathing.''

Her cracked lips quivered.

``Do you want to hear another story?''

While she waited for his answer, she drew a deep breath, hoping that it would ease some soreness in her body, though it little to remedy anything save highlight more aches. While attentively watching his face, the light flicked just so to make it look like a shallow nod.

``Okay, little king. If you want another story, I'll tell you another.''

She sat trying to think of what to recount. The choice, though, was not her own. The low candlelight in her periphery chose for her. She could feel her demons crawling in through the door and there was no pushing them out.

``I know that you've never asked how old I am, and to be quite frank, I don't know. You tend to not mind losing time when that's all you have. What I do remember, though, is that I wasn't that old when I first got married. Your dad wasn't my first husband.''

She recoiled at the thought of the man, but her mind couldn't pull away.

``I was still relatively young in the late 1700s, though I had already lived longer than most people ever would. As such, many people thought there was something unnatural about me; some kind of devil worship or witchcraft.

``Luckily I lived in a small community in Appalachia and  aside from queer gazes and snide remarks, people mostly left me to my own. But, out in the woods, there were no weird looks and there were no loudly whispered comments behind my back. I actually felt at peace when I was out in the woods, but looking back now, that probably didn't help my case.''

She paused a moment, slightly choking on the words being forced through her raspy throat. She reached for Kory's cup of water, but returned her hand to his when she saw that only dust filled the cup.

\textit{I'll fill that later, when I have some more energy.}

Coughing to relieve the itch in the back of her throat, she continued.

``One day, while I was out in the woods reading my favorite book, a boy from the town happened upon my sanctuary. I say boy, though he was in his late twenties.

``He was a bit of a strange one, in contrast to the other townsfolk. He didn't ever say strange things about me, nor did he look at me funny. Around him, I felt like just another, normal person.

``I had never really been in love before, and by his manners, I don't think he had either. He was so awkward that it was almost charming. Perhaps the thing that got me the most was that he called me darling.''

She stopped a moment and fidgeted in the chair, trying to find a comfortable position to continue her anecdote. The chair didn't allow her to sit any differently as the cushion had permanently contoured to her bad posture.

Uncomfortable and unsurprised, she went on.

``I won't bore you with our courtship, as there wasn't much special. In those days there weren't any movie theaters or nice restaurants to go eat at. Instead, most of our time together was spent talking. A crazy notion, I know.''

She looked at his face expecting a grin, but his neutral expression was only accented by the dancing candlelight.

\textit{I wish that you were awake. Please wake up soon so I can take care of you.}

``Excuse me. I lost myself in some thoughts for a bit.

``Right, dating. There really wasn't much and we soon got married. Since most of the townsfolk, including his parents were superstitious, no one attended the ceremony. It didn't bother us too much, as young love is blind.

``Jeremiah worked for his parents, helping out on their little farm and with the animals, but when we got married, he decided that he needed to move on and support his new family. So we moved to a larger town...

``Wait, did I not tell you his name earlier? No, I don't think that I did. His name was Jeremiah. His parents were devout protestants, though you wouldn't be able to tell from their hypocrisy.

``Anyway, we moved to a larger town where we could find work. I worked in a small textiles factory and he found work with the local railroading guild.

``For the next while, life was pretty uninteresting.''

She paused for a moment and found that she had taken her hand from Kory. Now her hands were in her lap, tightly clenched to the point that her knuckles were white and her dry skin was cracking.

\textit{Calm down. It's just a story now. It's all in the past. This part of your life is dead. It's just a story. It's just a story.}

A few deep, jagged breaths later, she composed herself.

``We had been away from his hometown, where we met, for a number of years, and Jeremiah wanted to go back for a visit. I reluctantly agreed as the people there were better left in the past, in my opinion. But, I supposed a wife shouldn't get in between a boy and his mother, save she wants to have the devil for an in-law.

``While we were there, we stayed with his parents and helped with their day-to-day tasks. Eyes were always on me, as it seemed that the townsfolk did not forget me. It even seemed they had grown more incorrigible.

``Seeing my discomfort, Jeremiah tried to find any excuse for us to take chores that got us out of town, and one evening, we went into the woods to collect firewood.''

She exerted herself and placed her hand on Kory's head.

``While we were out, Jeremiah and I spread out to find better tinder and logs to bring back. Then, before I could comprehend what was happening, I was on the ground, being mauled by a bear. The searing pain of its jaws biting into my shoulder and neck, the cold ripping of its claws across my stomach was enough to cause me to pass out.

``Later, when I came to, Jeremiah was sitting by my side. I was back at his parents' cabin. He let me know that I had been out for nearly a month.

``He didn't want to tell me about what happened, but after pressing him, he confided that when I was attacked by the bear, my screams and the sound of snapping bones alerted him. When he arrived on the scene, he shot the bear and came to my rescue.

``According to him, I looked like a child's ragdoll rolled in the mud. Bones protruded from my skin in multiple places and the ground was drenched in blood.''

She moved her hand to Kory's face and stroked his cheek.

\textit{I'm sure that when I passed out this last time, you were distraught to see my like that. I get it, and I'm sorry.}

``Jeremiah somehow got me back to his parents' house and there they treated me to the best of their abilities.

``Later the evening of when I woke, his mother asked `So, made another deal with the devil? He's letting you torment us a while longer?' I was livid. Jeremiah tried to convince me that his mother didn't mean what she was saying, but how could that be? To say something so vindictive and not mean it?

``Despite still having multiple broken bones and healing wounds, I convinced Jeremiah that we needed to leave, and so only about a week after waking up, we went back home to our lives in the bigger city.''

She stopped a moment as a coughing fit filled the room. When the coughing subsided, her chest quivered with each breath.

``Sorry, kiddo. Mom's just fine. Don't mind me.

``So, when we got back home, I noticed that there was something different about Jeremiah, like something was gnawing at the back of his mind.

``After a few months back at home, he confronted me one evening over dinner, and asked how I lived through the bear attack, if I actually did sell my soul to the devil.

``I was appalled that he would even entertain such thoughts. In my rage, I told him everything that I knew about myself in attempt to quell his curiosity, though it was just fuel to the flames.

``He reassured me that he loved me and that he wouldn't do anything to change that. I believed him because he had been nothing but true to his word all the years we had been married.''

She looked back over at the empty glass.

``I'm sorry, kiddo. Can you give me a second? Don't you dare wake up while I'm gone.''

With the glass in hand, she started her pilgrimage to the kitchen for water. When she made it to the doorway to Kory's room, she leaned against it to take a break. The chipped paint grabbed at her clothing and her feet felt like ice. She glanced over at the thermostat on the wall, only for her to discover that the tens digit had burned out, so the temperature was `four.'

\textit{Four? Seventy-four? Thirty-four? I can't tell when I run this thin. God, I need thicker socks. Later, I'll get those later.}

She continued down the hallway to the kitchen when she felt she had recovered enough, though she stumbled a few times, but at long last, she made it to the sink.

With the cup under the spout, she turned on the faucet. It sputtered and spat air between small bursts of water. It only filled the glass about halfway before her gut heaved her forward into the cabinet.

\textit{Fine. That's enough water.}

The cup slid around on her dry, chapped lips. As she tipped the cup to drink, water streamed down the sides of her mouth as well as into her throat. The water tasted fuzzy from all the dust, but the cooling sensation of it lining her stomach helped it unclench.

Bringing the glass back to the sink, she filled it up and returned to Kory's room with his refreshment.

When she sat, she leaned her head back and took a moment to recover her senses and remember her story.

``Jeremiah, as I said, was never the same after the bear attack. He was still loving and took care of me, but there was something off. A few months after I imparted all my secrets to him, in the light of our fireplace, he asked me a question that I will never forget: `Darling, can I cut you? Of course just for experimentation! To see how your gift works!'

``The question shocked me. He continued to explain that it would never be to hurt me and that we could quit any time I wanted. It obviously was important enough that he was willing to ask such a terrible thing, so I trusted him and acquiesced.

``He got out his bowie knife and slowly, all the while checking my face to see if it was alright, brought it to my forearm and surgically cut deep.'' She winced as she brought her hand to her forearm and rubbed the scar. ``I can still feel it. I can feel every scar I've ever got.''

She tried to cry, but was too dehydrated and instead breathed choppy breaths.

``After that day, his experiments grew more and more elaborate, supposedly in the pursuit of testing the extent of my gift. Over the years, my love and fondness for him evaporated and was replaced with pain and loathing; but his love for me grew and perverted into a sick, sadistic fantasy.

``In the end, after years of nearly dying month after month, he died. I won't say it was an accident, because it wasn't. Just, please, don't ever ask me to remember that story.''

She brought her legs up into the chair and folded her arms on her knees. Her dirty unkempt hair covered her elbows as she buried her face in her arms.

``Kory, I'm so sorry. I'm sorry that you have a witch for a mother. I promised a long time ago to not share my secrets with anyone, but I trust you completely. You, my king, would never hurt me, would you?''

The candlelight flicked the air as she sat there in silence, waiting to hear her boy's breath.

\line

% she recounts the loneliest times in her life, particularly the time between husbands when she had nothing/no one to live for

\storydate{FILL IN DATE}

``I'm here. I'm here. I'm here...''

Her eyes were closed and she continued mumbling. The silence in the room was still enough that she could hear her slow, faint heartbeat.

The cushion she sat on was now growing mold. The green walls were faded with age. All around, whispers of past demons filled the corners of the dead house, looming about every corner.

She tried to open her eyes, but they were too weak to obey.

She wiggled her fingers. To her surprise, she was still holding Kory's hand. His soft, supple hands were the only source of warmth that reached her.

Again, she tried to open her eyes.

\textit{My boy. I need to see my boy.}

This time, with added purpose, her eyes opened; one and then the other. The room was lit by a murky glow coming from the filthy desk window, which was cracked open ever so slightly. Dust hung in air and breathing seemed to coat her lungs, stifling her breath.

Her attention was fixed on her son. She sat there, motionless, watching his eyelids. The freckles there made a small triangle shape and through her bleary vision, they seemed to sway back and forth.

His face was the same one that was now burned into the forefront of her mind. \textit{His nose is just like his dad's. And his facial hair is so cute right now. I bet when he wakes up and grows it out, it'll look so nice.}

Her heartbeat sped up a bit thinking about Tom and her boy. With it, her tinnitus grew louder. She couldn't tell if the house was completely silent, or if the ringing in her ears was drowning out any sounds.

She tried to speak to Kory, for him to hear her voice, but she felt the sides of her mouth split. The sharp pain in contrast to her body's numbed state caused her to rethink her current ambitions.

Instead, she continued to sit in her chair; to continue her communion with life and death.

\textit{I need to talk to him. He needs to hear my voice. I need him to hear me.}

She exercised her mouth, opening and closing it gradually more and more to prevent additional injury.

\textit{Is there any water left?}

She glanced over at where the glass was supposed to be, but it wasn't there. To her surprise, she found it on the floor, broken.

\textit{It must have fallen from the table at some point. Did I bump it? I don't... remember.}

Without water, she knew talking would be difficult, so she redoubled her determination. She needed his company.

After what seemed an eternity, she finally felt like she could speak.

``Hey... Kory. I'm here.''

She swallowed hard to wet her dry throat, though it did little good.

``I don't really have anything to talk about. I'm sure there's something I can talk about, but...'' She reeled for a moment. ``I'm having a hard time remembering... anything.''

Her eyes started clearing up. She continued staring blankly at her son. His bed was sagging. It seemed as though it was trying to swallow him whole.

\textit{I need to say... something.}

She opened her mouth and started talking, not knowing where it would lead her.

``You look like you're sleeping. I can read you a bedtime story. Yeah, a bedtime story could be good. I'll read you my favorite book. It's the Canterbury Tales, by Chaucer.''

\textit{Yes that's a good book to read. I loved it when I was younger. Where is it? Where...}

Her mind pushed through the fog in her head, trying to remember where that book was located.

``I... think I lost it. Gone in a... fire. My cabin... on... fire.''

Her memory came to her slowly, but piece by piece, as her emotional state crumbled.

``I loved that book. Chaucer was my only friend. No one else loved me. No one else wanted to be with me.

``I was a witch and a murderer to everyone. They shunned me. My house... they burned my house.''

The memory caused her to choke on her words as she began to hyperventilate.

``I've lived so long. Alone so long. But... I knew there was something out in the world... for me. I knew that you would eventually... come to... me.''

She began to stand up to get closer to her son, but her atrophied legs couldn't support her. Instead of making it to the bed to be with him, she fell to the floor, landing on glass shards from the nearby broken glass.

``I was alone so long. No one cared. I didn't care. Loved ones came into my life and became monsters. Others came and died of old age. But me, something won't let me die. I know, I've tried. I've tried so many times.''

Her voice was now little more than a whisper. The cuts on her hands and face began to bleed, though her blood was thick from dehydration.

``You asked me before why I had so many scars.'' She removed her sweater as violently as she could in her anemic state and hoisted her body over the side of Kory's bed.

``Look! Look!'' she cried as she showed him her arms. ``Cutting your arms is supposed to let you bleed to death, but for me, I just pass out and wake up a few weeks later.''

Yanking her hair back, she showed him the faded, purple bruise around her neck. ``Hanging is supposed to break your neck, but me? It breaks my neck, but I hang there, lucid, until someone happens upon me and calls for help.''

Her blood stained the side of the bed, and when she noticed, she panicked.

``No, no, no. I can't let your get dirty. I... I have to clean this up.''

Again, she tried to stand, but immediately fell back to the floor in a crude mockery of prostration at the bed altar of her son. There on the filthy floor, little pools of her blood soaked up the dust and grime.

Her body ached and she wanted to curl up, but her revulsion with her body and the hundreds of scars it bore kept her from self-soothing.

``What do I have to live for? How long am I going to be kept here? You... you are why I'm still here. I have to be here for you.''

``So much of my life was empty. I wanted to die. I wanted to be included. Outcast... I was an outcast. Why... can't I just die? It would be so much easier.''

Her body feebly shook in the cold of the room. Extending her hand back to Kory's, she tried to embrace his warmth.

``I'm sorry. Your mother is a zombie, a shell of a human.''

What meager energy she may have had was now gone. She lied there on the floor for hours, muttering incoherently of past trauma.

``My life has been so empty. Please don't ever leave me.''

Something was listening. Between her sobs, she could hear the faint, rhythmic rapping of hundreds of fingers.

Her demons were back, and she knew they wouldn't let go.

\line

% she's visited

\storydate{FILL IN DATE}
