\documentclass[9pt]{memoir}
\usepackage{charter}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{csquotes}

% \usepackage[margin=1in]{geometry}
% \usepackage{indentfirst}


% \usepackage{parskip}
% \setlength{\parindent}{0 pt}
% \setlingth{\parskip}{1cm}

\title{Thy Cup Runneth Over}
\author{Andy Monk}
\date{}

\begin{document}

\clearpage
\maketitle
\thispagestyle{empty}

% synopsys: after having a strange encounter with a stranger at the grocery store, a man's mind continues to enlarge, but upon reaching the critical threshold of his mind's capacity, he begins to forget information about himself as the visions of the fledgling gods rush in


\frontmatter
% roman numberal numbering
% no default chapter number w/o *

% \tableofcontents

\mainmatter
% normal numbering
% default chapter number w/o *

Showing up to residential scenes where a dead body is involved were always her least favorite, right after missing children's cases. Pulling into the neighborhood, she thought to herself, \textit{Why can't I live in a place this nice?}. Each house looked like the ideal suburban American dream home: trimmed hedges, trees lining the drive ways, freshly cleaned walkways, windows so clean that they were hazardous to birds.

Rounding the last corner at her GPS's behest, she found the house plastered with the yellow tape, though her partner's worn Prius parked out front was also a dead giveaway that this was the place. She kept telling Lee that he needed to get a different car if he wanted any sort of street cred, but he, as always, would laugh it off saying that street cred didn't matter at his age and that she could have his share. Just the kind of answer you'd expect from a sixty-some-odd year old asian man that mildly resembled Buddha. Pulling in behind the Prius, she saw his signature bumper sticker \textit{Prius be Nice}. The obligatory eye roll swept across her face as she unintentionally re-read if for the hundredth time.

She pulled out her phone and rescanned the scant briefing they were given:

\vspace{1em}

\begin{displayquote}
    A woman identifying as Sloan Huffman called 911 earlier today (1:14 PM, January 17, 2014) reporting a dead body in her neighbor's home. When asked to provide further details, she became incoherent and could only provide the homeowner's name and address.

    Resident name: Philip Crawford

    Address: 234 NW Kensington St
\end{displayquote}

\vspace{1em}

Now that she was closer, she could feel that something was off with this house, even just glancing at it. Sure, the lawn was unkempt and there was a pile of delivery boxes sitting on the front porch, but there was something else going on. Looking at the home, everything seemed normal until she tried focusing on her periphery. Were the windows moving? Glancing over to the movement stopped them dead and made her wonder if she had had enough coffee. Still, there was something irksome that didn't sit well, and it was most certainly eminating from the house.

``Hey! You finally made it. Had a hard time finding the place with your fancy phone?'' Lee's bellow startled her out of her trance enough to make her spill some of her coffee, though none got on her clothes.

``Nah, I was thinking that I wanted to be sick today and thought about letting you do some work for a change.''

``Ha! Would you like a rundown of what I've found so far, or are you secretly telepathic now?''

``Still working on that. How about you give me that rundown.''

``Sure thing.''

``''


\backmatter
% normal numbering
% no default chapter number w/o *


\end{document}
