\documentclass[9pt]{memoir}
\usepackage{charter}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{csquotes}

\usepackage{indentfirst}
\setlength{\parindent}{1em}
\setlength{\parskip}{.7em}
\renewcommand{\baselinestretch}{1.2}
\renewcommand{\line}{\noindent \rule{\textwidth}{1pt} \vspace{1em}}

\raggedbottom

\title{I'm Here}
\author{Jonathan Vuyk}
\date{}

%*--- Custom Commands -----------------------------------------------------------------------------
\newcommand{\storydate}[1]{\noindent \textbf{#1} \vspace{2em}}
%*-------------------------------------------------------------------------------------------------

\begin{document}

\pagecolor{black}
\color{gray}

\clearpage
\maketitle
\thispagestyle{empty}

% synopsys: two lifelong friends, one with time travel abilities and the other seemingly immortal, get locked into fates worse than death

% notes:
% mother:
    % Name:
    % Power:
% son:
    % Name: Korinth Jacobsen, Kory for short, but mother often calls her little king (reference to Sisyphus who was the king of Corinth who was forced to push a rock up a hill endlessly for his sin of cheating death multiple times)
    % Power: time travel, but has limited control over it (another parallel to pushing the rock?)


\frontmatter
% roman numberal numbering
% no default chapter number w/o *
% \tableofcontents

%! arcane/cryptic prose about the futility of living forever (get reader to believe that it's about the mother)
%! somehow hint at it being one of the post-its from "thy cup runneth over"

\begin{displayquote}

    Query not the desires of man, to hold aloft alien constructs. You know not what you desire, yet that is what you seek. We are naught. THEY are all. THEY are grand. To catch the pearls of eternity is to bear new shackles for we are slaves to Grandfather Time.

    Die today for tomorrow is yesterday. Die today and relinquish your meat to his feast. Grandfather Time laughs. He gorges on all. Live and be spoiled. Live and be subject to He Who Holds.

\end{displayquote}

\begin{flushright}

    City of Kidale Evidence Collections; Case 4451, Item 10223 \hspace{2em}

\end{flushright}


\mainmatter
% normal numbering
% default chapter number w/o *

\chapter*{Denial}
%! he's finally old enough to talk to his mother about his abilities and see what the ramifications are, but he doesn't want them

\storydate{7: January 14, 1998}

``Hey, I'm here.''

Everything was dark and fuzzy. Rather, his mind was fuzzy. He could, however, feel something constricted around his left hand.

``Take your time. You're going to feel foggy for a bit, okay?''

The voice sounded muddled, dry, and distand. He tried opening his eyes to see who it was, but they felt swollen. Instead he rolled around a bit. The constriction around his hand lifted, pulling him into an upright position.

\textit{Thank goodness mom's here. I must have passed out again.}

Once he was sitting up, he felt his mom scratching his back. It sent tingles up his spine, enough to make him shiver. Finally one eye peaked open and the other followed suit. The room was dimly lit and quiet. Glancing around, he saw the silhouette of his mother sitting next to him on the bed. Everything was familiar: multiple pictures of Mario on the muted green walls, a little TV on the floor with the N64 next to it. One thing that was a little strange was that the room was clean.

\textit{Where are my drawings and colored pencils? Mom probably knows.}

He looked back at his mom. She looked tired but happy. Her brunet hair was in a ponytail today which accented her already tired, stretched eyes.

``Kory? Do you want something to eat?''

``Colored pencils. Do you know where my colored pencils are?''

``I don't think you'll want to eat your colored pencils. I put them away, but we can color after you've eaten. What would you like?''

``Uh, waffles?'' His words felt sticky as he pushed them from his mouth.

``Sure, little king. Do you need anything else? You should probably try getting up, going to the bathroom, and washing your face. Take your time though. You were out for a bit this time.''

``Really? Oh, okay.''

She stood up and left the room, but her hand caressed the doorframe as she glanced a weary smile back in his direction.

He still felt quite foggy, but more alert than he was just a few minutes prior.

\textit{What should I draw later? A robot? That's fighting the moon? Yeah! And the moon has a laser sword with...}

Kory clutched his head softly as it began throbbing. Now he noticed that his throat was pretty sore too. Luckily, on the bedside table was a glass of water.

\textit{Man, mom's the best.}

Drinking the water felt sharp as it made its way down, but it made his stomach feel cool. Still quite tired, he laid back down and closed his eyes again listening to the clatter of cooking from the kitchen. Sensation was making its way back to the rest of his body; his hands felt little needles and now he could wiggle his toes. Waking up from these fainting spells were tedious, but at least they didn't scare him any more. One thing that came sooner than he wanted was the sensation to go to the bathroom.

Hopping out of bed, he found that his legs weren't as stable as he thought and stumbled sideways into his night stand, spilling the mostly full glass. Before he could replant himself, his mother came rushing in to help.

``Are you okay?'' she asked with a mild panic on her face.

``I still have rubber legs.''

She forced a small smile and giggled with him. Once she could see that he was stable, she reaffirmed that he was okay and let him go to do what he needed. As he left the room, he looked back and found her on the floor cleaning up the water that he spilled with her apron. In that moment, she seemed very old, though he knew that couldn't be right.

\line

Their modest kitchen swirled with the magical aromas of bacon and warm syrup as Kory found his way to the table. From the kitcken, his mother asked, ``How many waffles would you like? One or two?''

``Two? Cut up please?''

``Of course. You are my little King after all!''

He watched his mom pull one waffle from the iron and then another from a nearby plate onto the cutting board. There she used her magical knife skills to turn the circular waffles into square pieces. Kory had tried cutting his own waffles on numerous occasions, but they were nowhere near as good as his mom's, so he was content to let her do it for him. Maybe someday when he's bigger he'll be able to do things like her.

With two plates in hand, she made her way to the table and placed and returned to the kitchen for the orange juice and her coffee. As she sat down, he could see the biggest smile on her face. He knew that she was the happiest person in the world because she was always so cheery and positive, even when she was visibly tired.

Looking at his plate, he could see the two waffles cut up as requested, but the were mostly shoved off to one side. The majority of the plate was covered in bacon.

``Eat up, kiddo. I know you love bacon, so don't be shy.''

He moved his attention to his mother's plate.

``Mom, why don't you have any waffles? Do you want some of mine?''

``Oh no, honey. Silly me forgot to go grocery shopping, so we had less stuff than I thought. You go ahead and eat. I'm not that hungry.''

Placated, he returned his attention to his own plate and began eating.

For a while, there was just silence as he ate and his mother watched, occasionally sipping her coffee, until the grandfather clock in their house chimed. Kory loved to count along with the strums to find out the time.

\textit{One, two, three, four, five, six, seven, eight, nine. No more? Nine in the morning I guess.}

He looked up from his plate that was nearly empty at this point and realized that he probably ate too much. His mother was still watching him with a weary smirk that somehow confused him.

``What are we doing today? Are we going to learn some more about the culolonimus clouds and rain? We didn't finish that lesson last week.''

His mom sat up in her chair and processed what she just heard. He clearly forgot about coloring already, but she remembered that she had things to do too.

``It's cumulonimbus, silly goose,'' she corrected slowly, ``but you actually reminded me of someone that I need to call. They wanted to talk to you.''

She stood up and walked to the phone in the kitchen and dialed from a paper she had stashed nearby. He couldn't really hear the conversation, other than the stray sentence or phrase like ``yeah, he's awake,'' and ``when do you think you'll have an opening?''

\textit{What do they want to talk about? I guess I do know a lot about pretty much everything.}

Kory was trying desperately to find room to fit his last two slices of bacon in his stomach when his mom walked back in.

``So, honey, I have some questions that are going to seem kind of weird.''

``I like weird!''

``Differend kind of weird, little king. Do you remember what we were doing before you passed out this time?''

``Not really. I think we were studying. Was it English? Those adjective things are hard.''

``I think we were doing social studies that day, but no, you were out in the back yard playing.''

``Okay?'' he said hesitantly.

``Do you remember what yesterday's date was?''

``Thursday!''

She gave a half-hearted chuckle. ``No, silly. Like month, day, and year.''

He thought for a minute. ``October 14th? 1996?''

``Okay. So I was just on the phone with a nice lady named Dr. Hall. She's an abilities counselor.''

``Oh, didn't Paul from down the street go and talk to one of those last year?''

``He did. You have a very good memory! I didn't even remember that he and his dad went to see someone. I've been meaning for you to go for a while, but I know that these kinds of doctors can be kind of hard to understand so I wanted to wait until you a little older. Luckily Dr. Hall is very accomodating. She said to call when you woke up and that she'd make time for you.''

``What's she like?''

``She said that she has a thirty minute slot open in the afternoon, so we can meet her together and find out what she's like.''

``Oh. Okay. So we're not going to play or study today?''

``I don't think so. You just take it easy and have some fun before we go.''

Kory didn't really understand what was going on, but he did realize he had room for the rest of his bacon now.

\line

Kory hated sitting in waiting rooms. They felt too open and clean. The exam rooms were better as the walls were closer. Something about the disarray of chairs and magazines made him uneasy. He clenched his mom's hand and closed his eyes.

``Korinth Jacobsen?'' asked a nicely dressed lady standing in the opening of a short hallway.

``That's us,'' whispered his mother as she stood up.

The two of them made their way over, all the while the woman watched with a warm smile. Kory looked up at the strange woman. She was wearing purple horn rimmed glasses.

\textit{Those are funny glasses.}

``Is it okay if I come in or are these usually done one on one?'' his mother inquired as soon as they were within polite talking distance.

``You're free to come in if he wants it. Otherwise, you can wait out here. It shouldn't take long. As I said on the phone, these meetings usually only take about thirty minutes.''

Kory's mother knelt down next to him and held his shoulders. ``Would you like me to come in with you? You're just going to talk to Dr. Hall here for a little bit.''

He didn't really know what was going on but having his mother nearby always made him feel more at ease. ``Will you come in?''

``Of course. I'm always here for you.''

``Wonderful! Follow me back to my office,'' urged Dr. Hall.

With that, they all headed down the hall and entered a room at the end on the left. The inside of the room was nothing like what Kory expected. He thought they were going to see a doctor.

\textit{Where's the exam chair with the paper? Why is there carpet in here? Why are there pictures of papers with writing on them rather than the cool posters about the brain and stuff?}

Kory was so distracted that he didn't hear Dr. Hall invite him to sit and kept gawking at the room.

\textit{There are plants in here! They're growing all over. Look at that one. Its vines are growing up and around the window! Do you think she has dirt in h...}

Suddenly he was pulled from his stupor by his mother's hand on his shoulder.

``Kory, sit down please,'' she said as she patted the leather love seat where she was sitting.

Once he was settled, Dr. Hall began.

``So, Korinth, would you prefer I call you Kory like your mom, or something else?''

``Kory is good. I like Kory. It's easier to spell than Korinth.''

``I'd have to agree with you on that one. And how old are you, Kory?''

``I'm seven, almost eight!''

''Congrats! Eight is when you become the man of the house, isn't it?''

That seemed like a weird statement. He was the man of the house as dad wasn't around.

Dr. Hall noticed him make a little bit of a funny face at the retort and brushed it off with a small shake of her head. ``Do you know why you're here or what I do?''

``I know that one of our neighbors came to visit someone like you, right mom?''

His mom gave an approving nod before he returned his attention to the doctor.

``Good. Well, let me try to explain a little bit more about what I do. I'm what you call an abilities counselor. As you may or may not know, there are many people that have powers that are kind of like super powers from your comics and TV shows! Usually these powers are nowhere near as powerful and tend to be a problem for people rather than making them Superman.''

``But I thought you were a doctor? Do superheroes need doctors?'' Kory was a bit overwhelmed with this doctor not needing to taking his temperature and growing plants all around the room.

``I'm a different kind of doctor. Not a medical doctor. I talk to people and try to help them cope with their abilities and find normalcy in the day to day. Does that make sense?''

``I think so. So, you're like Batman's butler who helps Bruce Wayne do all his normal things while he goes out and beats up the bad guys?''

``Almost. I help people be comfortable with their powers.''

``I see. But I don't have any powers. Are you going to give me some? I want spider webs like Peter Parker!''

``I can't give you powers. Honestly, the latest research doesn't even know why or how some people have them in the first place!''

Dr. Hall made strange eye contact with Kory's mom as if to ask something to which his mom provided a small confused shrug.

``Kory. Your mom called us a while back asking us to meet you because we're pretty sure that you \textit{do} have an ability.''

The thought of having an ability gave Kory chills up his back.

\textit{What could my power be? It has to be something cool. Laser eyes? Am I super strong? Can I walk on walls?}

The counselor smirked a bit as she could see the flurry in his mind, but pulled him back to reality.

``Kory. Your mom told us about your symptoms, which I want to confirm with you, but we're fairly certain that you have body/self dissociation.''

\textit{I have what?}

``I can see that you're confused, and to be honest, it's one of the more confusing abilities that's out there. Let me start by asking you some questions and try to help you connect some dots. Do you know what today's date is?''

\textit{Again with this question? Why are adults so fascinated by the date and the weather?}

``Uh, my mom already asked me this earlier. It's October 14th. 1996.''

Dr. Hall nodded. ``Has your mother told you what today's actual date is?''

``Why would she?'' replied Kory as concern crept into his countenance.

``Kory. Today is January 14th 1998.''

The silence hung like the plants over Dr. Hall's windows. Kory looked down at his hands and started counting.

``You mean I've been asleep for fifteen months? My super power is sleeping?''

Dr. Hall's eyes beamed as she pushed the purple glasses up her nose.

``Actually, you're not sleeping! This is where it actually gets really fascinating! In the case for normal people, when the go to sleep, their body continues to metabolize and their brain function continues. This is even largely true for people in comas. For people like you, which coincidentally are few, your body doesn't seem to metabolize and there's zero brain activity! There are a number of theories but most of them stem from Descartes, Leibniz, and Spinoza. In their works they rationalized that there is a distinction between the self and the body. In most cases, the line is quite blurred. It can also be dangerous in some cases such as depressive dissociation, where the person believes that they are experiencing their own life as a third party observer. An out-of-body experience, if you will.''

\textit{None of this makes sense. How could I just not have fifteen months? Where did they go? I was awake yesterday. I had breakfast. I played in my room. I did my homework. Yesterday. It was all yesterday.}

Dr. Hall continued. ``For you, however, there seems to be an additional level of dissociation! As I said, the current theories are that the self and the body actually disconnect for some undetermined amount of time. During that time, the body enters a stasis of sorts and ceases all function, but oddly enough retains warmth and a few other traits that indicate that the individual isn't dead.''

``Doctor!'' interjected his mom, though it did little to wake the doctor from her frenzied excitement.

``The question is, what happens to the self during this time? Where is it? Is it tangible? These are some of the fundamental questions that still haven't been answered by philosophers \textit{or} physicists. What is understood, however, is that the individual doesn't seem to know either and wakes up when the two reunite, seemingly with no break in their understanding of time, despite considerable time passing. It's almost like time travelling!''

\textit{So I can time travel?}

Kory glanced over at his mother to get some affirmation of what he should be feeling. She looked angry, but he wasn't sure why. He didn't really want to be there anymore either as this lady was weird and scary.

``Dr. Hall. Are you a counselor or an academic?''

``Actually, I'm both! I would love to continue studying your son as this ability is quite rare. When he has another episode, call us and we can bring all of the equipment to your home and figure out what's going on! Then when he wakes up, we can get him on a regimen of sessions and medications and see where that takes us, but this is all very exciting stuff. Wouldn't you agree, Kory?'' She stared big eyed at Kory like he was a meal.

Kory's mom put her arm around him and pulled him in close.

When he didn't respond, she continued, ``In the meantime, we could set up some sort of...''

His mom cut her off. ``No, I don't want my son poked and prodded when he's so vulnerable.''

``Oh please. When they're having an episode, they're hardly even human.''

\textit{What? Now I'm not human?}

Kory felt tears start to well in his eyes as his mother shot up. He had never seen his mother like this. She turned and grabbed his hand. ``Let's go, honey. Dr. Hall isn't really interested in helping. She just wants to publish another paper.''

Confused, Dr. Hall timidly raised her arms as if to beg for reconsideration.

\textit{Paper? Time travelling, I'm not human, and now paper? What's going on?}

Wiping the tears that began rolling down his face, the two of them started for the door.

``Mrs. Jacobsen. Please think about it and call me. I won't charge for today's meeting. As for you, Kory, it was a pleasure meeting you!''


\chapter*{Anger}
%! Kory's angry that he has to time skip and refuses to do so and skips uncontrollably

\storydate{10: April 20, 2008}

``Hey, Kiddo. I'm here.''

\textit{Another blackout. I hate these. Wonder how long I was out this time.}

He ran through his current options.

\textit{I haven't moved yet, so mom probably doesn't know I've woken up yet. She's probably just talking to try to get me to wake up. I could just lie here and pretend to be asleep. That certainly seems like a better option to waking up and pretending that this is no big deal.}

With his mind made up, he stayed in bed, unmoving.

``You know, as your mom, I do know a thing or two.''

\textit{What do you know? Do you have to put up with this stupid ``ability''?}

``Like, for instance, I know that when you're time travelling or in stasis or whatever we're going to call it, you don't breathe. Why don't you get up and talk to me? I have a surprise lined up for you.''

He mulled his new options around for a bit. After thinking for a bit, he decided to hold his breath.

``You goose! You can't fool me!'' she exclaimed as she pounced and began tickling him.

Impulse swept in and his abs contracted, shooting his legs into the air. Gasping for air, he pleaded for her to stop.

Once she stopped, he looked over at her. She had a wide, warm smile on. Her hair was in a braid today which showed her ears, but also accentuated a bandaid on her forehead.

\textit{Mom must have hit her head one something.}

All of a sudden, he remembered that he was grumpy and that he didn't like being happy. The smile on his face disappeared and his brows furrowed.

``Oh come on. What's wrong?''

He continued to pout for a minute, but soon started to feel the pangs of waking. His head began pounding and needles radiated through his limbs. He didn't want his mom to watch him while he took a moment in the fetal position.

``Hey, mom. Do you think that we could have pancakes?'' he asked in attempt to get his mom to leave the room.

``Sure, king, but you probably haven't noticed that it's eight pm.''

He turned as best he could and glanced out the window. Outside his window, he could see his dogwood in bloom and behind it, sure enough, were the stars.

``I want pancakes.''

He couldn't think of much else as he wanted her out, but didn't want to hurt her feelings.

``Okay okay. I'll go start making some pancakes. Would you like some bacon with that too?''

He stammered a bit. ``Ye... yes please.''

She got up from the bed slowly as the smile faded from her face.

\textit{I'm not sure how long I was out this time, but I'm sure that she has no idea how I feel. Waking up is terrible. Everything hur...}

He stopped mid thought as a stabbing pain pierced his chest. Curling up on his bed helped the pain a bit and after a few seconds, it abated. Clutching his chest, he sat back up on his bed to finally take a look around. Sure enough, not much had changed. The walls were still a forest green color, most of the mario posters were taken down, and a desk sat in the corner with various magazines and papers strewn about.

\textit{I hate this ability. Why do I have to have it! It's ruining everything! I didn't even know what time it was!}

He noticed that his fists were clenched and teeth grit, so he tried taking some deep breaths, though that proved more difficult than not. The air seemed sharp as he expanded his lungs and air he expelled felt stale. He glanced over at his desk again. Nothing seemed to have moved on his desk, even though the rest of the room was clearly cleaned. Without second thought, he stood up and walked over to the chair and sat to examine his desktop.

Surely enough, everything was right where it would have been had he only been asleep for the night. Right on top were the envelopes and hand drawn invitations that he had been working on.

\textit{I don't even get to have a birthday.}

The thought caused tears to well up in his eyes. Looking back down, he blinked hard and two tear made their way down his little cheeks.

``Hey, little king. Your pancakes are ready. Are you feeling okay?'' The soft touch of her hand on his hair made him jump a little.

Quickly he ran his arm across his face to remove his fresh tears. ``I'm fine,'' he retorted as he stood up to leave the room.

At the table, he found a plate with a stack of three pancakes. Scattered throughout their surface were little blackish blotches. He couldn't tell if they were chocolate chips or blueberries until he got closer and sat down. They were chocolate chips. He probably would have lost it had they been blueberries.

His mom languidly made her way into the kitchen, poured herself a cup of coffee, and sat herself adjacent.

``Hey, Kory. I know that you're having a tough time, but you know, we'll figure out this ability stuff together.''

He didn't want to listen, but unfortunately the food was in the same room as her. In protest, he tried using his utinsels loudly, but within reasonable noise levels. Aside from the clanking of his fork on the plate, they sat in silence until he was done.

Her gaze scarcely broke from him and he could feel it. It moved around from his hair to his feet. She was inspecting him. Slowly.

``Kory, I...''

``What do you know about these stupid abilities! What do you know about how we're going to work through this? What if I don't want to work through this? I just want to be normal! I want to go to school with other kids, not home schooled. I want to know that tomorrow is going to be tomorrow and not two years from now. I want to wake up and not feel like I'm dying. I want to have a birthday party!''

The last point broke him and he began to weep.

``How long was I asleep this time, mom?'' The question was forced through tears, snot, and gasps.

Shocked, she took a moment to realize what had just happened.

``Kory,'' she said even more softly than before and wrapping her arms around his shoulders, ``I'm sorry that this is hard and that I can't take it away. Please know that I'm trying and that I'll do anything for you.''

He laid his head into her shoulder. A few strands of hair pulled from her braid and fell on his face. It was warm and he knew he was safe. Her breathing was slow and labored like she hadn't slept the night before, but there they stayed a moment.

Words kept spilling out of his mouth as his brain tried to conjure something to say, but his thoughts were incoherent.

``Shhh...'' she whispered. ``Do you remember that I said I have a surprise lined up for you earlier? I think it's better that I don't keep it too much a surprise.''

He perked up at the thought.

\textit{What did she get me?}

``I called a bunch of people that I know that have kids around your age, and I invited them to come over for a birthday party for you.''

He picked his head up and glanced at her with questioning eyes, but she responded with a frail smile and crescent eyes.

Suddenly she perked up. ``You know, it's pretty hard to plan birthdays for you, but we'll always make the best of it!''

His mood dissipated at her joke and he returned to his cheerful self. ``When is it going to be?''

``This Saturday at eleven o'clock.''

The thought energized his brain.

\textit{Should I finish the birthday invites? How many kids are coming? What presents are they going to bring? What are we going to play? It's going to be at eleven o'clock? That means we'll probably eat lunch too! What are we going to eat? I hope we have bacon.}

``Can we have bacon?''

``What?''

``At the party?''

``Sure,'' she chuckled, ``anything for my king.''

``What date should I write on the invitations? Did you see the ones that I was making on my desk?''

``I did see them! They are very good. You should write `Saturday, April 22, 2008' on them.''

He could tell that a weight had been taken off his mom, but he couldn't help hearing that the year was 2008.

\line




\chapter*{Bargaining}
%! tries to understand if there's a way that he can live without the consequences of his condition
%! namely through time travelling backwards and talks through the implications/possibilities with his mom
%! eventually comes to the conclusion that it's too dangerous as it's too unknown



\chapter*{Depression}
%! mother gets hurt and the son is forced to deal with the consequences because it's the first time that he's really needing to come to grips with her condition
%! learns more about "abilities" and their tiering and how he and his mother are very low in their respective abilities



\chapter*{Acceptance}
%! terrible accident concerning mother putting her actual mortality into question
%! he stays with her as long as he can, but eventually needs to make a decision and chooses to time skip backwards
%! finds out that hes reliving a concrete past
%! comes to accept that this is his fate for eternity



\chapter*{Purpose}
%! only chapter from mother's point of view - waiting for her son to come out of stasis (where we learn what he's like during a time skip)
%! she's completely not taking care of herself as it is an undisclosed time into the future
%! learn that the mother has been dealing with the depression of knowing that living forever is not a blessing and will have to carry the heartbreak of getting close to others
%! reveal that the mother knows of, but does not know, the monster that stalks them
%! story ends with it speaking

How long had it been? She opened her eyes to the gaunt arms stretched in front of her. In their hands were her little king's warm hands. Were these her arms? How long \textit{had} it been? She didn't even recognize her own limbs.

Then the sharp stabbing pain of hunger threw her into convulsions as her stomach wretched to expell anything, though nothing came. Curled over, she gasped for air between convulsions, though she made sure to not release Kory's hands. She had to be here if he woke up.

Slowly her gut settled and just the gnawing pain of emaciation remained. Raising her heavy head, she looked upon her son. He looked exactly as he always had, not a single thing wrong, just as though he were asleep. His tawny, roughly cut hair lay to one side and the mild scruff that lay upon his face reminded her of his father. When had her little boy grown up?


\backmatter
% normal numbering
% no default chapter number w/o *


\end{document}
